---
title: "Internet use and mental health"
author: "Yan Luo"
date: '2023-10-01'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Make sure the working directory is "your path/internet-use-mental-health"
knitr::opts_knit$set(root.dir = "D:/github_project/internet-use-mental-health")

library(tidyverse)
library(haven)
library(sjlabelled)
library(mice)
library(tictoc)
library(doParallel)

```

# Self-constructed functions

```{r}

reverse_code <- function(x) {
  max_val <- max(x, na.rm = T)
  return(max_val - x + 1)
}

```

# Import data

## 2015-2016 - 2019-2020 cohort core questionnaire

```{r}

# 2015-2016
elsi_w1 <- read_dta(str_c(getwd(), "/data/raw/elsi/ELSI English (baseline) stata13.dta")) %>%
  mutate(
    .keep = "none",
    ## Basic information
    id, idhousehold, cohort = "elsi", country = 76, wave = 2015,
    
    ## Exposure variables
    internet_yes = case_when(
      p76 == 0 ~ "no",
      p76 == 1 ~ "yes",
      TRUE ~ NA_character_
    ),
    internet_yes = relevel(factor(internet_yes), ref = "no"),

    ## Outcomes
    depres = ifelse(r2 %in% c(8,9), NA, r2), effort = ifelse(r3 %in% c(8,9), NA, r3), 
    sleepr = ifelse(r4 %in% c(8,9), NA, r4), whappy = ifelse(r5 %in% c(8,9), NA, 1-r5), 
    flone = ifelse(r6 %in% c(8,9), NA, r6), enlife = ifelse(r7 %in% c(8,9), NA, 1-r7), 
    fsad = ifelse(r8 %in% c(8,9), NA, r8), going = ifelse(r9 %in% c(8,9), NA, r9), # CES-D 8
    shlt = case_when(
      n1 %in% c(0,1) ~ 5,
      n1 == 2 ~ 4,
      n1 == 3 ~ 3,
      n1 == 4 ~ 2,
      n1 == 5 ~ 1,
      TRUE ~ NA_real_
    ), # self-rated health
    satlife = ifelse(s18 %in% c(88,99), NA, s18), # Life satisfaction
    
    ## Covariates
    # Demographics
    age, 
    male = ifelse(sex == 0, "female", "male"), male = relevel(factor(male), ref = "female"),
    nonmarried = case_when(
      e7 == 2 ~ "no",
      e7 %in% c(1,3,4) ~ "yes",
      TRUE ~ NA_character_
      ),
    nonmarried = relevel(factor(nonmarried), ref = "no"),
    hhres = ar6, 
    
    # Socioeconomic status
    atotb = assets,
    lowedu = case_when(
      e22 %in% c(15:18) ~ "tertiary",
      e22 %in% c(10:14) ~ "secondary",
      e22 %in% c(1:9) ~ "primary",
      TRUE ~ NA_character_
    ),
    lowedu = relevel(factor(lowedu), ref = "tertiary"),
    lbrf = case_when(
      i1 == 1 ~ "employed",
      i1 == 0 & i5 == 1 ~ "retired",
      i1 == 0 & i5 %in% c(2:7) ~ "others",
      TRUE ~ NA_character_
    ), 
    lbrf = relevel(factor(lbrf), ref = "employed"),

    # Health Behaviors
    smoken = case_when(
      l30 == 3 ~ "no",
      l30 %in% c(1:2) ~ "yes",
      TRUE ~ NA_character_
      ),
    smoken = relevel(factor(smoken), ref = "no"),
    weekdrink = case_when(
      l24 %in% c(1:2) ~ "no",
      l24 == 3 & l25 == 0 ~ "no",
      l24 == 3 & l25 %in% c(1:7) ~ "yes",
      TRUE ~ NA_character_
    ),
    weekdrink = relevel(factor(weekdrink), ref = "no"),
    vgactx = ifelse(l9 == 9, NA, l9), mdactx = ifelse(l7 == 9, NA, l7), 
    phyinact = case_when(
      vgactx %in% c(1:7) | mdactx %in% c(1:7) ~ "no",
      vgactx == 0 & mdactx == 0 ~ "yes",
      TRUE ~ NA_character_
    ),
    phyinact = relevel(factor(phyinact), ref = "no"),
    
    # Physical health
    hibpe = case_when(
      n28 == 0 ~ 0,
      n28 %in% c(1:2) ~ 1,
      TRUE ~ NA_real_
    ),
    diabe = case_when(
      n35 == 0 ~ 0,
      n35 %in% c(1:2) ~ 1,
      TRUE ~ NA_real_
    ),
    cancre = ifelse(n60 == 9, NA, n60), lunge = ifelse(n55 == 9, NA, n55), 
    asthmae = ifelse(n54 == 9, NA, n54), arthre = ifelse(n56 == 9, NA, n56), 
    hearte = case_when(
      n46 == 1 | n48 == 1 | n50 == 1 ~ 1,
      n46 == 9 & n48 == 9 & n50 == 9 ~ NA_real_,
      TRUE ~ 0
    ),
    stroke = ifelse(n52 == 9, NA, n52),
    psyche = ifelse(n59 == 9, NA, n59), parkine = ifelse(n62 == 9, NA, n62), 
    alzhe = ifelse(n63 == 9, NA, n63), # Chronic diseases
    psyche = factor(psyche, labels = c("no", "yes")), 
    psyche = relevel(factor(psyche), ref = "no"),
    parkine = factor(parkine, labels = c("no", "yes")), 
    parkine = relevel(factor(parkine), ref = "no"),
    alzhe = factor(alzhe, labels = c("no", "yes")), 
    alzhe = relevel(factor(alzhe), ref = "no"),
    
    walkra = case_when(
      p37 == 1 ~ 0,
      p37 %in% c(2:4) ~ 1,
      TRUE ~ NA_real_
    ),
    dressa = case_when(
      p40 == 1 ~ 0,
      p40 %in% c(2:4) ~ 1,
      TRUE ~ NA_real_
    ),
    batha = case_when(
      p43 == 1 ~ 0,
      p43 %in% c(2:4) ~ 1,
      TRUE ~ NA_real_
    ),
    eata = case_when(
      p46 == 1 ~ 0,
      p46 %in% c(2:4) ~ 1,
      TRUE ~ NA_real_
    ),
    beda = case_when(
      p49 == 1 ~ 0,
      p49 %in% c(2:4) ~ 1,
      TRUE ~ NA_real_
    ),
    toilta = case_when(
      p55 == 1 ~ 0,
      p55 %in% c(2:4) ~ 1,
      TRUE ~ NA_real_
    ), # ADLs
    
    mealsa = case_when(
      p20 == 1 ~ 0,
      p20 %in% c(2:4) ~ 1,
      TRUE ~ NA_real_
    ), 
    moneya = case_when(
      p22 == 1 ~ 0,
      p22 %in% c(2:4) ~ 1,
      TRUE ~ NA_real_
    ), 
    transporta = case_when(
      p24 == 1 ~ 0,
      p24 %in% c(2:4) ~ 1,
      TRUE ~ NA_real_
    ), 
    shopa = case_when(
      p26 == 1 ~ 0,
      p26 %in% c(2:4) ~ 1,
      TRUE ~ NA_real_
    ), 
    phonea = case_when(
      p28 == 1 ~ 0,
      p28 %in% c(2:4) ~ 1,
      TRUE ~ NA_real_
    ), 
    medsa = case_when(
      p30 == 1 ~ 0,
      p30 %in% c(2:4) ~ 1,
      TRUE ~ NA_real_
    ) # IADLs
  )

# 2019-2020
elsi_w2 <- read_dta(str_c(getwd(), "/data/raw/elsi/ELSI English (2nd wave) stata13.dta")) %>%
  mutate(
    .keep = "none",
    ## Basic information
    id = as.numeric(str_remove(id2, "2020")), idhousehold = idhousehold2, cohort = "elsi", country = 76, wave = 2019,
    ## Exposure variables
    internet_yes = case_when(
      p76 == 0 ~ "no",
      p76 == 1 ~ "yes",
      TRUE ~ NA_character_
    ),
    internet_yes = relevel(factor(internet_yes), ref = "no"),

    ## Outcomes
    depres = ifelse(r2 %in% c(8,9), NA, r2), effort = ifelse(r3 %in% c(8,9), NA, r3), 
    sleepr = ifelse(r4 %in% c(8,9), NA, r4), whappy = ifelse(r5 %in% c(8,9), NA, 1-r5), 
    flone = ifelse(r6 %in% c(8,9), NA, r6), enlife = ifelse(r7 %in% c(8,9), NA, 1-r7), 
    fsad = ifelse(r8 %in% c(8,9), NA, r8), going = ifelse(r9 %in% c(8,9), NA, r9), # CES-D 8
    shlt = case_when(
      n1 %in% c(0,1) ~ 5,
      n1 == 2 ~ 4,
      n1 == 3 ~ 3,
      n1 == 4 ~ 2,
      n1 == 5 ~ 1,
      TRUE ~ NA_real_
    ), # self-rated health
    satlife = ifelse(s18 %in% c(88,99), NA, s18), # Life satisfaction
    
    ## Covariates
    # Demographics
    age, 
    male = ifelse(sex == 0, "female", "male"), male = relevel(factor(male), ref = "female"),
    nonmarried = case_when(
      e7 == 2 ~ "no",
      e7 %in% c(1,3,4) ~ "yes",
      TRUE ~ NA_character_
      ),
    nonmarried = relevel(factor(nonmarried), ref = "no"),
    hhres = nresidents, 
    
    # Socioeconomic status
    atotb = assets,
    lowedu = case_when(
      e22 %in% c(15:18) ~ "tertiary",
      e22 %in% c(10:14) ~ "secondary",
      e22 %in% c(1:9) ~ "primary",
      TRUE ~ NA_character_
    ),
    lowedu = relevel(factor(lowedu), ref = "tertiary"),
    lbrf = case_when(
      i0_28 == 1 ~ "employed",
      i0_28 == 0 & i0_30 == 1 ~ "retired",
      i0_1 == 0 | (i0_28 == 0 & i0_30 %in% c(2:7)) ~ "others",
      TRUE ~ NA_character_
    ), 
    lbrf = relevel(factor(lbrf), ref = "employed"),

    # Health behaviors
    smoken = case_when(
      l30_0 == 2 ~ "no",
      l30_0 == 1 & l30 == 3 ~ "no",
      l30_0 == 1 & l30 %in% c(1:2) ~ "yes",
      TRUE ~ NA_character_
      ),
    smoken = relevel(factor(smoken), ref = "no"),
    weekdrink = case_when(
      l24 %in% c(1:2) ~ "no",
      l24 == 3 & l25 == 0 ~ "no",
      l24 == 3 & l25 %in% c(1:7) ~ "yes",
      TRUE ~ NA_character_
    ),
    weekdrink = relevel(factor(weekdrink), ref = "no"),
    vgactx = ifelse(l9 == 9, NA, l9), mdactx = ifelse(l7 == 9, NA, l7), 
    phyinact = case_when(
      vgactx %in% c(1:7) | mdactx %in% c(1:7) ~ "no",
      vgactx == 0 & mdactx == 0 ~ "yes",
      TRUE ~ NA_character_
    ),
    phyinact = relevel(factor(phyinact), ref = "no"),
    
    # Physical health
    hibpe = case_when(
      n28 == 0 ~ 0,
      n28 %in% c(1:2) ~ 1,
      TRUE ~ NA_real_
    ),
    diabe = case_when(
      n35 == 0 ~ 0,
      n35 %in% c(1:2) ~ 1,
      TRUE ~ NA_real_
    ),
    cancre = ifelse(n60 == 9, NA, n60), lunge = ifelse(n55 == 9, NA, n55), 
    asthmae = ifelse(n54 == 9, NA, n54), arthre = ifelse(n56 == 9, NA, n56), 
    hearte = case_when(
      n46 == 1 | n48 == 1 | n50 == 1 ~ 1,
      n46 == 9 & n48 == 9 & n50 == 9 ~ NA_real_,
      TRUE ~ 0
    ),
    stroke = ifelse(n52 == 9, NA, n52),
    psyche = ifelse(n59 == 9, NA, n59), parkine = ifelse(n62 == 9, NA, n62), 
    alzhe = ifelse(n63 == 9, NA, n63), # Chronic diseases
    psyche = factor(psyche, labels = c("no", "yes")), 
    psyche = relevel(factor(psyche), ref = "no"),
    parkine = factor(parkine, labels = c("no", "yes")), 
    parkine = relevel(factor(parkine), ref = "no"),
    alzhe = factor(alzhe, labels = c("no", "yes")), 
    alzhe = relevel(factor(alzhe), ref = "no"),
    
    walkra = case_when(
      p37 == 0 ~ 0,
      p37 == 1 ~ 1,
      TRUE ~ NA_real_
    ),
    dressa = case_when(
      p40 == 0 ~ 0,
      p40 == 1 ~ 1,
      TRUE ~ NA_real_
    ),
    batha = case_when(
      p43 == 0 ~ 0,
      p43 == 1 ~ 1,
      TRUE ~ NA_real_
    ),
    eata = case_when(
      p46 == 0 ~ 0,
      p46 == 1 ~ 1,
      TRUE ~ NA_real_
    ),
    beda = case_when(
      p49 == 0 ~ 0,
      p49 == 1 ~ 1,
      TRUE ~ NA_real_
    ),
    toilta = case_when(
      p55 == 0 ~ 0,
      p55 == 1 ~ 1,
      TRUE ~ NA_real_
    ), # ADLs
    
    mealsa = case_when(
      p20 == 0 ~ 0,
      p20 == 1 ~ 1,
      TRUE ~ NA_real_
    ), 
    moneya = case_when(
      p22 == 0 ~ 0,
      p22 == 1 ~ 1,
      TRUE ~ NA_real_
    ), 
    transporta = case_when(
      p24 == 0 ~ 0,
      p24 == 1 ~ 1,
      TRUE ~ NA_real_
    ), 
    shopa = case_when(
      p26 == 0 ~ 0,
      p26 == 1 ~ 1,
      TRUE ~ NA_real_
    ), 
    phonea = case_when(
      p28 == 0 ~ 0,
      p28 == 1 ~ 1,
      TRUE ~ NA_real_
    ), 
    medsa = case_when(
      p30 == 0 ~ 0,
      p30 == 1 ~ 1,
      TRUE ~ NA_real_
    ) # IADLs
  )

```


# Variable definition

```{r}

# Define variables
tidy_elsi <- bind_rows(elsi_w1, elsi_w2) %>%
  rowwise() %>%
  mutate(
    dis = sum(c(hibpe, diabe, cancre, lunge, hearte, stroke, arthre), na.rm = T),
    dis_miss = sum(is.na(c(hibpe, diabe, cancre, lunge, hearte, stroke, arthre)), na.rm = F),
    adl = sum(c(dressa, batha, eata, beda, toilta, walkra), na.rm = T),
    adl_miss = sum(is.na(c(dressa, batha, eata, beda, toilta, walkra)), na.rm = F),
    iadl = sum(c(moneya, medsa, shopa, mealsa, phonea), na.rm = T),
    iadl_miss = sum(is.na(c(moneya, medsa, shopa, mealsa, phonea)), na.rm = F),
  ) %>%
  ungroup() %>%
  mutate(
    iwy = NA, iwm = NA,
    dis = ifelse(dis_miss == 7, NA, dis), 
    adl = ifelse(adl_miss == 6, NA, adl),
    iadl = ifelse(iadl_miss == 5, NA, iadl),
    adl_any = ifelse(adl == 0, "no", "yes"), adl_any = relevel(factor(adl_any), ref = "no")
  ) %>%
  remove_all_labels() %>%
  zap_formats()

rm(elsi_w1, elsi_w2)

length(unique(tidy_elsi$id)) # 9949

```


# Generate analytic samples

## Internet use (yes/no)

```{r}

# Keep participants aged >=50 years
id_50plus <- tidy_elsi %>%
  group_by(id) %>%
  slice(1) %>%
  ungroup() %>%
  filter(age >= 50) %>%
  pull(id)

filter_50plus <- tidy_elsi %>%
  filter(id %in% id_50plus)
length(unique(filter_50plus$id)) # 9949

# Keep participants with complete data on internet use at baseline
id_iyes <- filter_50plus %>%
  group_by(id) %>%
  slice(1) %>%
  ungroup() %>%
  filter(!is.na(internet_yes)) %>%
  pull(id)

filter_iyes <- filter_50plus %>%
  filter(id %in% id_iyes)
length(unique(filter_iyes$id)) # 9945

# Keep participants with complete data on outcomes at baseline
## Depressive symptoms
id_cesd_bl <- filter_iyes %>%
  rowwise() %>%
  mutate(
    cesd_miss = sum(is.na(c(depres, flone, effort, sleepr, whappy, fsad, going, enlife)), na.rm = F)
  ) %>%
  ungroup() %>%
  mutate(
    with_cesd = ifelse(cesd_miss == 0, 1, 0)
  ) %>%
  group_by(id) %>%
  slice(1) %>%
  filter(with_cesd == 1) %>% 
  ungroup() %>%
  pull(id)

## Self-rated health
id_shlt_bl <- filter_iyes %>%
  mutate(
    with_shlt = ifelse(!is.na(shlt), 1, 0)
  ) %>%
  group_by(id) %>%
  slice(1) %>%
  filter(with_shlt == 1) %>% 
  ungroup() %>%
  pull(id)

## Life satisfaction
id_satlife_bl <- filter_iyes %>%
  mutate(
    with_satlife = ifelse(!is.na(satlife), 1, 0)
  ) %>%
  group_by(id) %>%
  slice(1) %>%
  filter(with_satlife == 1) %>% 
  ungroup() %>%
  pull(id)

id_ot_bl <- intersect(id_cesd_bl, id_shlt_bl) # 8783
id_ot_bl <- intersect(id_ot_bl, id_satlife_bl) # 8629

filter_ot_bl <- filter_iyes %>%
  filter(id %in% id_ot_bl)
length(unique(filter_ot_bl$id)) # 8629

# Keep participants with at least one-wave complete data on outcomes over follow-ups
id_2obs <- filter_ot_bl %>%
  group_by(id) %>%
  filter(n() >= 2) %>%
  dplyr::slice(1) %>%
  ungroup() %>%
  pull(id)

filter_2obs <- filter_ot_bl %>%
  filter(id %in% id_2obs)
length(unique(filter_2obs$id)) # 8136

## Depressive symptoms
id_cesd <- filter_2obs %>%
  rowwise() %>%
  mutate(
    cesd_miss = sum(is.na(c(depres, flone, effort, sleepr, whappy, fsad, going, enlife)), na.rm = F)
  ) %>%
  ungroup() %>%
  mutate(
    with_cesd = ifelse(cesd_miss == 0, 1, 0)
  ) %>%
  group_by(id) %>%
  slice(2:n()) %>%
  mutate(
    t_with_cesd = cumsum(with_cesd)
    ) %>%
  slice(n()) %>%
  filter(t_with_cesd >= 1) %>% 
  ungroup() %>%
  pull(id)

## Self-rated health
id_shlt <- filter_2obs %>%
  mutate(
    with_shlt = ifelse(!is.na(shlt), 1, 0)
  ) %>%
  group_by(id) %>%
  slice(2:n()) %>%
  mutate(
    t_with_shlt = cumsum(with_shlt)
    ) %>%
  slice(n()) %>%
  filter(t_with_shlt >= 1) %>% 
  ungroup() %>%
  pull(id)

## Life satisfaction
id_satlife <- filter_2obs %>%
  mutate(
    with_satlife = ifelse(!is.na(satlife), 1, 0)
  ) %>%
  group_by(id) %>%
  slice(2:n()) %>%
  mutate(
    t_with_satlife = cumsum(with_satlife)
    ) %>%
  slice(n()) %>%
  filter(t_with_satlife >= 1) %>% 
  ungroup() %>%
  pull(id)

id_ot <- intersect(id_cesd, id_shlt) # 7056
id_ot <- intersect(id_ot, id_satlife) # 6775

filter_ot <- filter_2obs %>%
  filter(id %in% id_ot)
length(unique(filter_ot$id)) # 6775

# Keep participants without dementia and psychological diseases at baseline
id_mental <- filter_ot %>%
  group_by(id) %>%
  slice(1) %>%
  ungroup() %>%
  filter(parkine == "yes" | alzhe == "yes" | psyche == "yes") %>%
  pull(id)

filter_nomental <- filter_ot %>%
  filter(!id %in% id_mental) 
length(unique(filter_nomental$id)) # 5529

# Keep participants with complete data on covariates at baseline
id_cov <- filter_nomental %>%
  rowwise() %>%
  mutate(
    cov_miss = sum(is.na(c(age, male, atotb, lowedu, lbrf, nonmarried, hhres, smoken, weekdrink, phyinact, dis, adl_any, iadl)), na.rm = F)
  ) %>%
  ungroup() %>%
  mutate(
    with_cov = ifelse(cov_miss == 0, 1, 0)
  ) %>%
  group_by(id) %>%
  slice(1) %>%
  ungroup() %>%
  filter(with_cov == 1) %>%
  pull(id)

filter_cov <- filter_ot %>%
  filter(id %in% id_cov) %>%
  rowwise() %>%
  mutate(
    cesd = sum(c(depres, flone, effort, sleepr, whappy, fsad, going, enlife), na.rm = F)
  ) %>%
  ungroup()
length(unique(filter_cov$id)) # 4178

table(filter_cov %>% group_by(id) %>% summarise(count = n()) %>% pull(count))

# Final
bl <- filter_cov %>% 
  group_by(id) %>% 
  slice(1) %>%
  ungroup() %>%
  mutate(
    .keep = "none",
    id, internet_yes, 
    age, male, lowedu, lowwealth = factor(reverse_code(ntile(atotb, 4))), lbrf, 
    nonmarried, hhres, smoken, weekdrink, phyinact,
    dis, adl_any, iadl
    )

final <- filter_cov %>%
  group_by(id) %>%
  mutate(
    fisrt = first(wave),
    cwave = wave - fisrt
  ) %>%
  ungroup() %>%
  mutate(
    .keep = "none",
    id, country, iwy, iwm, wave,
    cesd, shlt, satlife, 
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife),
    cwave
  ) %>%
  dplyr::select(
    id, country, iwy, iwm, wave,
    cesd, shlt, satlife,
    cesd_stand, shlt_stand, satlife_stand,
    cwave
  )

final_iyes_elsi <- final %>% 
  left_join(., bl, by = "id") %>%
  mutate(
    id = str_c("elsi_", id)
  )

rm(bl, final)
rm(list = ls()[str_detect(string = ls(), pattern = "id_")])
rm(list = ls()[str_detect(string = ls(), pattern = "filter_")])

```

# Subgroup analyses: Internet use (yes/no)

## By age

```{r}

# 50-64 years
middle_iyes_elsi <- final_iyes_elsi %>%
  filter(age < 65) %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

# ≥65 years
old_iyes_elsi <- final_iyes_elsi %>%
  filter(age >= 65) %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

```

## By gender

```{r}

# Male
male_iyes_elsi <- final_iyes_elsi %>%
  filter(male == "male") %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

# Female
female_iyes_elsi <- final_iyes_elsi %>%
  filter(male == "female") %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

```

## By marital status

```{r}

# Married
married_iyes_elsi <- final_iyes_elsi %>%
  filter(nonmarried == "no") %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

# Unmarried
nonmarried_iyes_elsi <- final_iyes_elsi %>%
  filter(nonmarried == "yes") %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

```

## By education

```{r}

# Primary
pedu_iyes_elsi <- final_iyes_elsi %>%
  filter(lowedu == "primary") %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

# Secondary
sedu_iyes_elsi <- final_iyes_elsi %>%
  filter(lowedu == "secondary") %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

# Tertiary
tedu_iyes_elsi <- final_iyes_elsi %>%
  filter(lowedu == "tertiary") %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

```

## By household wealth

```{r}

# Low
lwealth_iyes_elsi <- final_iyes_elsi %>%
  filter(lowwealth == 3) %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

# Middle
mwealth_iyes_elsi <- final_iyes_elsi %>%
  filter(lowwealth == 2) %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

# High
hwealth_iyes_elsi <- final_iyes_elsi %>%
  filter(lowwealth == 1) %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

```

## By labor force status

```{r}

# Working
work_iyes_elsi <- final_iyes_elsi %>%
  filter(lbrf == "employed") %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

# Retired
retired_iyes_elsi <- final_iyes_elsi %>%
  filter(lbrf == "retired") %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

# Others
others_iyes_elsi <- final_iyes_elsi %>%
  filter(lbrf == "others") %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

```

## By current smoking 

```{r}

# Current smoking
smoke_iyes_elsi <- final_iyes_elsi %>%
  filter(smoken == "yes") %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

# No smoking
nosmoke_iyes_elsi <- final_iyes_elsi %>%
  filter(smoken == "no") %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

```

## By alcohol consumption

```{r}

# Weekly alcohol use
drink_iyes_elsi <- final_iyes_elsi %>%
  filter(weekdrink == "yes") %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

# Less than weekly alcohol use
nodrink_iyes_elsi <- final_iyes_elsi %>%
  filter(weekdrink == "no") %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )


```

## By physical activity

```{r}

# Physical inactivity
phyinact_iyes_elsi <- final_iyes_elsi %>%
  filter(phyinact == "yes") %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

# Physical activity
phyact_iyes_elsi <- final_iyes_elsi %>%
  filter(phyinact == "no") %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

```

## By ADL disability

```{r}

# ADL disability
adl_iyes_elsi <- final_iyes_elsi %>%
  filter(adl_any == "yes") %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

# No ADL limitation
noadl_iyes_elsi <- final_iyes_elsi %>%
  filter(adl_any == "no") %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

```

## By chronic conditions

```{r}

# ≥1 chronic conditions
dis_iyes_elsi <- final_iyes_elsi %>%
  filter(dis > 0) %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

# No chronic conditions
nodis_iyes_elsi <- final_iyes_elsi %>%
  filter(dis == 0) %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

```


# Sentivity analyses: Multiple imputation

## Internet use (yes/no)

```{r}

# There is no missing value in this dataset

```

# Save data

```{r}

save(
  final_iyes_elsi, # Main analyses
  middle_iyes_elsi, old_iyes_elsi, male_iyes_elsi, female_iyes_elsi,
  pedu_iyes_elsi, sedu_iyes_elsi, tedu_iyes_elsi,
  lwealth_iyes_elsi, mwealth_iyes_elsi, hwealth_iyes_elsi,
  work_iyes_elsi, retired_iyes_elsi, others_iyes_elsi,
  smoke_iyes_elsi, nosmoke_iyes_elsi, drink_iyes_elsi, nodrink_iyes_elsi,
  married_iyes_elsi, nonmarried_iyes_elsi,
  phyinact_iyes_elsi, phyact_iyes_elsi, adl_iyes_elsi, noadl_iyes_elsi,
  dis_iyes_elsi, nodis_iyes_elsi, # Subgroup analyses
  file = str_c(getwd(), "/data/processed/elsi_processed_data.RData", sep = "")
  )

```
