---
title: "Internet use and mental health"
author: "Yan Luo"
date: '2023-10-01'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Make sure the working directory is "your path/internet-use-mental-health"
knitr::opts_knit$set(root.dir = "E:/Multiple cohort study/Harmonized Data FIile/HarmonizedSurveyData/internet_use_mental/internet-use-mental-health")

library(tidyverse)
library(haven)
library(sjlabelled)
library(mice)
library(tictoc)
library(doParallel)
library(gtsummary)

```

# Self-constructed functions

```{r}

reverse_code <- function(x) {
  max_val <- max(x, na.rm = T)
  return(max_val - x + 1)
}

```

# Import data

## 2015-2016 - 2019-2020 cohort core questionnaire

```{r}

# 2015-2016
elsi_w1 <- read_dta(str_c(getwd(), "/data/raw/elsi/ELSI English (baseline) stata13.dta")) %>%
  mutate(
    .keep = "none",
    ## Basic information
    id, idhousehold, cohort = "elsi", country = 76, wave = 2015,
    iwy = as.numeric(format(as.Date(ar4), "%Y")), 
    iwm = as.numeric(format(as.Date(ar4), "%m")),
    
    ## Exposure variables
    internet_yes = case_when(
      p76 == 0 ~ "no",
      p76 == 1 ~ "yes",
      TRUE ~ NA_character_
    ),
    internet_yes = relevel(factor(internet_yes), ref = "no"),

    ## Outcomes
    depres = ifelse(r2 %in% c(8,9), NA, r2), effort = ifelse(r3 %in% c(8,9), NA, r3), 
    sleepr = ifelse(r4 %in% c(8,9), NA, r4), whappy = ifelse(r5 %in% c(8,9), NA, 1-r5), 
    flone = ifelse(r6 %in% c(8,9), NA, r6), enlife = ifelse(r7 %in% c(8,9), NA, 1-r7), 
    fsad = ifelse(r8 %in% c(8,9), NA, r8), going = ifelse(r9 %in% c(8,9), NA, r9), # CES-D 8
    shlt = case_when(
      n1 %in% c(0,1) ~ 5,
      n1 == 2 ~ 4,
      n1 == 3 ~ 3,
      n1 == 4 ~ 2,
      n1 == 5 ~ 1,
      TRUE ~ NA_real_
    ), # self-rated health
    satlife = ifelse(s18 %in% c(88,99), NA, s18), # Life satisfaction
    
    ## Covariates
    # Demographics
    age, 
    male = ifelse(sex == 0, "female", "male"), male = relevel(factor(male), ref = "female"),
    nonmarried = case_when(
      e7 == 2 ~ "no",
      e7 %in% c(1,3,4) ~ "yes",
      TRUE ~ NA_character_
      ),
    nonmarried = relevel(factor(nonmarried), ref = "no"),
    hhres = ar6,
    contact = case_when(
      p70 == 0 ~ "no",
      p70 == 1 ~ "yes",
      TRUE ~ NA_character_
    ),
    contact = relevel(factor(contact), ref = "no"),
    
    # Socioeconomic status
    atotb = assets,
    lowedu = case_when(
      e22 %in% c(15:18) ~ "tertiary",
      e22 %in% c(10:14) ~ "secondary",
      e22 %in% c(1:9) ~ "primary",
      TRUE ~ NA_character_
    ),
    lowedu = relevel(factor(lowedu), ref = "tertiary"),
    lbrf = case_when(
      i1 == 1 ~ "employed",
      i1 == 0 & i5 == 1 ~ "retired",
      i1 == 0 & i5 %in% c(2:7) ~ "others",
      TRUE ~ NA_character_
    ), 
    lbrf = relevel(factor(lbrf), ref = "employed"),

    # Health Behaviors
    smoken = case_when(
      l30 == 3 ~ "no",
      l30 %in% c(1:2) ~ "yes",
      TRUE ~ NA_character_
      ),
    smoken = relevel(factor(smoken), ref = "no"),
    weekdrink = case_when(
      l24 %in% c(1:2) ~ "no",
      l24 == 3 & l25 == 0 ~ "no",
      l24 == 3 & l25 %in% c(1:7) ~ "yes",
      TRUE ~ NA_character_
    ),
    weekdrink = relevel(factor(weekdrink), ref = "no"),
    vgactx = ifelse(l9 == 9, NA, l9), mdactx = ifelse(l7 == 9, NA, l7), 
    phyinact = case_when(
      vgactx %in% c(1:7) | mdactx %in% c(1:7) ~ "no",
      vgactx == 0 & mdactx == 0 ~ "yes",
      TRUE ~ NA_character_
    ),
    phyinact = relevel(factor(phyinact), ref = "no"),
    
    # Physical health
    hibpe = case_when(
      n28 == 0 ~ 0,
      n28 %in% c(1:2) ~ 1,
      TRUE ~ NA_real_
    ),
    diabe = case_when(
      n35 == 0 ~ 0,
      n35 %in% c(1:2) ~ 1,
      TRUE ~ NA_real_
    ),
    cancre = ifelse(n60 == 9, NA, n60), lunge = ifelse(n55 == 9, NA, n55), 
    asthmae = ifelse(n54 == 9, NA, n54), arthre = ifelse(n56 == 9, NA, n56), 
    hearte = case_when(
      n46 == 1 | n48 == 1 | n50 == 1 ~ 1,
      n46 == 9 & n48 == 9 & n50 == 9 ~ NA_real_,
      TRUE ~ 0
    ),
    stroke = ifelse(n52 == 9, NA, n52),
    psyche = ifelse(n59 == 9, NA, n59), parkine = ifelse(n62 == 9, NA, n62), 
    alzhe = ifelse(n63 == 9, NA, n63), # Chronic diseases
    psyche = factor(psyche, labels = c("no", "yes")), 
    psyche = relevel(factor(psyche), ref = "no"),
    parkine = factor(parkine, labels = c("no", "yes")), 
    parkine = relevel(factor(parkine), ref = "no"),
    alzhe = factor(alzhe, labels = c("no", "yes")), 
    alzhe = relevel(factor(alzhe), ref = "no"),
    
    walkra = case_when(
      p37 == 1 ~ 0,
      p37 %in% c(2:4) ~ 1,
      TRUE ~ NA_real_
    ),
    dressa = case_when(
      p40 == 1 ~ 0,
      p40 %in% c(2:4) ~ 1,
      TRUE ~ NA_real_
    ),
    batha = case_when(
      p43 == 1 ~ 0,
      p43 %in% c(2:4) ~ 1,
      TRUE ~ NA_real_
    ),
    eata = case_when(
      p46 == 1 ~ 0,
      p46 %in% c(2:4) ~ 1,
      TRUE ~ NA_real_
    ),
    beda = case_when(
      p49 == 1 ~ 0,
      p49 %in% c(2:4) ~ 1,
      TRUE ~ NA_real_
    ),
    toilta = case_when(
      p55 == 1 ~ 0,
      p55 %in% c(2:4) ~ 1,
      TRUE ~ NA_real_
    ), # ADLs
    
    mealsa = case_when(
      p20 == 1 ~ 0,
      p20 %in% c(2:4) ~ 1,
      TRUE ~ NA_real_
    ), 
    moneya = case_when(
      p22 == 1 ~ 0,
      p22 %in% c(2:4) ~ 1,
      TRUE ~ NA_real_
    ), 
    transporta = case_when(
      p24 == 1 ~ 0,
      p24 %in% c(2:4) ~ 1,
      TRUE ~ NA_real_
    ), 
    shopa = case_when(
      p26 == 1 ~ 0,
      p26 %in% c(2:4) ~ 1,
      TRUE ~ NA_real_
    ), 
    phonea = case_when(
      p28 == 1 ~ 0,
      p28 %in% c(2:4) ~ 1,
      TRUE ~ NA_real_
    ), 
    medsa = case_when(
      p30 == 1 ~ 0,
      p30 %in% c(2:4) ~ 1,
      TRUE ~ NA_real_
    ) # IADLs
  )


# The interview date is missing in the 2nd wave and replace with the median of the follow-up period (from August 2019 to March 2021, https://www.ncbi.nlm.nih.gov/pmc/articles/PMC9908056/).
"2020-06"

# 2019-2020
elsi_w2 <- read_dta(str_c(getwd(), "/data/raw/elsi/ELSI English (2nd wave) stata13.dta")) %>%
  mutate(
    .keep = "none",
    ## Basic information
    id = as.numeric(str_remove(id2, "2020")), idhousehold = idhousehold2, cohort = "elsi", country = 76, wave = 2019, iwy = 2020, iwm = 6,
    
    ## Exposure variables
    internet_yes = case_when(
      p76 == 0 ~ "no",
      p76 == 1 ~ "yes",
      TRUE ~ NA_character_
    ),
    internet_yes = relevel(factor(internet_yes), ref = "no"),

    ## Outcomes
    depres = ifelse(r2 %in% c(8,9), NA, r2), effort = ifelse(r3 %in% c(8,9), NA, r3), 
    sleepr = ifelse(r4 %in% c(8,9), NA, r4), whappy = ifelse(r5 %in% c(8,9), NA, 1-r5), 
    flone = ifelse(r6 %in% c(8,9), NA, r6), enlife = ifelse(r7 %in% c(8,9), NA, 1-r7), 
    fsad = ifelse(r8 %in% c(8,9), NA, r8), going = ifelse(r9 %in% c(8,9), NA, r9), # CES-D 8
    shlt = case_when(
      n1 %in% c(0,1) ~ 5,
      n1 == 2 ~ 4,
      n1 == 3 ~ 3,
      n1 == 4 ~ 2,
      n1 == 5 ~ 1,
      TRUE ~ NA_real_
    ), # self-rated health
    satlife = ifelse(s18 %in% c(88,99), NA, s18), # Life satisfaction
    
    ## Covariates
    # Demographics
    age, 
    male = ifelse(sex == 0, "female", "male"), male = relevel(factor(male), ref = "female"),
    nonmarried = case_when(
      e7 == 2 ~ "no",
      e7 %in% c(1,3,4) ~ "yes",
      TRUE ~ NA_character_
      ),
    nonmarried = relevel(factor(nonmarried), ref = "no"),
    hhres = nresidents,  
    contact = case_when(
      p70 == 0 ~ "no",
      p70 == 1 ~ "yes",
      TRUE ~ NA_character_
    ),
    contact = relevel(factor(contact), ref = "no"),
    
    # Socioeconomic status
    atotb = assets,
    lowedu = case_when(
      e22 %in% c(15:18) ~ "tertiary",
      e22 %in% c(10:14) ~ "secondary",
      e22 %in% c(1:9) ~ "primary",
      TRUE ~ NA_character_
    ),
    lowedu = relevel(factor(lowedu), ref = "tertiary"),
    lbrf = case_when(
      i0_28 == 1 ~ "employed",
      i0_28 == 0 & i0_30 == 1 ~ "retired",
      i0_1 == 0 | (i0_28 == 0 & i0_30 %in% c(2:7)) ~ "others",
      TRUE ~ NA_character_
    ), 
    lbrf = relevel(factor(lbrf), ref = "employed"),

    # Health behaviors
    smoken = case_when(
      l30_0 == 2 ~ "no",
      l30_0 == 1 & l30 == 3 ~ "no",
      l30_0 == 1 & l30 %in% c(1:2) ~ "yes",
      TRUE ~ NA_character_
      ),
    smoken = relevel(factor(smoken), ref = "no"),
    weekdrink = case_when(
      l24 %in% c(1:2) ~ "no",
      l24 == 3 & l25 == 0 ~ "no",
      l24 == 3 & l25 %in% c(1:7) ~ "yes",
      TRUE ~ NA_character_
    ),
    weekdrink = relevel(factor(weekdrink), ref = "no"),
    vgactx = ifelse(l9 == 9, NA, l9), mdactx = ifelse(l7 == 9, NA, l7), 
    phyinact = case_when(
      vgactx %in% c(1:7) | mdactx %in% c(1:7) ~ "no",
      vgactx == 0 & mdactx == 0 ~ "yes",
      TRUE ~ NA_character_
    ),
    phyinact = relevel(factor(phyinact), ref = "no"),
    
    # Physical health
    hibpe = case_when(
      n28 == 0 ~ 0,
      n28 %in% c(1:2) ~ 1,
      TRUE ~ NA_real_
    ),
    diabe = case_when(
      n35 == 0 ~ 0,
      n35 %in% c(1:2) ~ 1,
      TRUE ~ NA_real_
    ),
    cancre = ifelse(n60 == 9, NA, n60), lunge = ifelse(n55 == 9, NA, n55), 
    asthmae = ifelse(n54 == 9, NA, n54), arthre = ifelse(n56 == 9, NA, n56), 
    hearte = case_when(
      n46 == 1 | n48 == 1 | n50 == 1 ~ 1,
      n46 == 9 & n48 == 9 & n50 == 9 ~ NA_real_,
      TRUE ~ 0
    ),
    stroke = ifelse(n52 == 9, NA, n52),
    psyche = ifelse(n59 == 9, NA, n59), parkine = ifelse(n62 == 9, NA, n62), 
    alzhe = ifelse(n63 == 9, NA, n63), # Chronic diseases
    psyche = factor(psyche, labels = c("no", "yes")), 
    psyche = relevel(factor(psyche), ref = "no"),
    parkine = factor(parkine, labels = c("no", "yes")), 
    parkine = relevel(factor(parkine), ref = "no"),
    alzhe = factor(alzhe, labels = c("no", "yes")), 
    alzhe = relevel(factor(alzhe), ref = "no"),
    
    walkra = case_when(
      p37 == 0 ~ 0,
      p37 == 1 ~ 1,
      TRUE ~ NA_real_
    ),
    dressa = case_when(
      p40 == 0 ~ 0,
      p40 == 1 ~ 1,
      TRUE ~ NA_real_
    ),
    batha = case_when(
      p43 == 0 ~ 0,
      p43 == 1 ~ 1,
      TRUE ~ NA_real_
    ),
    eata = case_when(
      p46 == 0 ~ 0,
      p46 == 1 ~ 1,
      TRUE ~ NA_real_
    ),
    beda = case_when(
      p49 == 0 ~ 0,
      p49 == 1 ~ 1,
      TRUE ~ NA_real_
    ),
    toilta = case_when(
      p55 == 0 ~ 0,
      p55 == 1 ~ 1,
      TRUE ~ NA_real_
    ), # ADLs
    
    mealsa = case_when(
      p20 == 0 ~ 0,
      p20 == 1 ~ 1,
      TRUE ~ NA_real_
    ), 
    moneya = case_when(
      p22 == 0 ~ 0,
      p22 == 1 ~ 1,
      TRUE ~ NA_real_
    ), 
    transporta = case_when(
      p24 == 0 ~ 0,
      p24 == 1 ~ 1,
      TRUE ~ NA_real_
    ), 
    shopa = case_when(
      p26 == 0 ~ 0,
      p26 == 1 ~ 1,
      TRUE ~ NA_real_
    ), 
    phonea = case_when(
      p28 == 0 ~ 0,
      p28 == 1 ~ 1,
      TRUE ~ NA_real_
    ), 
    medsa = case_when(
      p30 == 0 ~ 0,
      p30 == 1 ~ 1,
      TRUE ~ NA_real_
    ) # IADLs
  )

```


# Variable definition

```{r}

# Define variables
tidy_elsi <- bind_rows(elsi_w1, elsi_w2) %>%
  rowwise() %>%
  mutate(
    dis = sum(c(hibpe, diabe, cancre, lunge, hearte, stroke, arthre), na.rm = T),
    dis_miss = sum(is.na(c(hibpe, diabe, cancre, lunge, hearte, stroke, arthre)), na.rm = F),
    adl = sum(c(dressa, batha, eata, beda, toilta, walkra), na.rm = T),
    adl_miss = sum(is.na(c(dressa, batha, eata, beda, toilta, walkra)), na.rm = F),
    iadl = sum(c(moneya, medsa, shopa, mealsa, phonea), na.rm = T),
    iadl_miss = sum(is.na(c(moneya, medsa, shopa, mealsa, phonea)), na.rm = F),
  ) %>%
  ungroup() %>%
  mutate(
    dis = ifelse(dis_miss == 7, NA, dis), 
    adl = ifelse(adl_miss == 6, NA, adl),
    iadl = ifelse(iadl_miss == 5, NA, iadl),
    adl_any = ifelse(adl == 0, "no", "yes"), adl_any = relevel(factor(adl_any), ref = "no")
  ) %>%
  remove_all_labels() %>%
  zap_formats()

rm(elsi_w1, elsi_w2)

length(unique(tidy_elsi$id)) # 9949

```


# Generate analytic samples

## Internet use (yes/no)

```{r}

# Keep participants aged >=50 years
id_50plus <- tidy_elsi %>%
  group_by(id) %>%
  slice(1) %>%
  ungroup() %>%
  filter(age >= 50) %>%
  pull(id)

filter_50plus <- tidy_elsi %>%
  filter(id %in% id_50plus)
length(unique(filter_50plus$id)) # 9949

# Keep participants with complete data on internet use at baseline
id_iyes <- filter_50plus %>%
  group_by(id) %>%
  slice(1) %>%
  ungroup() %>%
  filter(!is.na(internet_yes)) %>%
  pull(id)

filter_iyes <- filter_50plus %>%
  filter(id %in% id_iyes)
length(unique(filter_iyes$id)) # 9945

# Keep participants with complete data on outcomes at baseline
## Depressive symptoms
id_cesd_bl <- filter_iyes %>%
  rowwise() %>%
  mutate(
    cesd_miss = sum(is.na(c(depres, flone, effort, sleepr, whappy, fsad, going, enlife)), na.rm = F)
  ) %>%
  ungroup() %>%
  mutate(
    with_cesd = ifelse(cesd_miss == 0, 1, 0)
  ) %>%
  group_by(id) %>%
  slice(1) %>%
  filter(with_cesd == 1) %>% 
  ungroup() %>%
  pull(id)

## Self-rated health
id_shlt_bl <- filter_iyes %>%
  mutate(
    with_shlt = ifelse(!is.na(shlt), 1, 0)
  ) %>%
  group_by(id) %>%
  slice(1) %>%
  filter(with_shlt == 1) %>% 
  ungroup() %>%
  pull(id)

## Life satisfaction
id_satlife_bl <- filter_iyes %>%
  mutate(
    with_satlife = ifelse(!is.na(satlife), 1, 0)
  ) %>%
  group_by(id) %>%
  slice(1) %>%
  filter(with_satlife == 1) %>% 
  ungroup() %>%
  pull(id)

id_ot_bl <- intersect(id_cesd_bl, id_satlife_bl) # 8649
length(unique(id_ot_bl))
id_ot_bl <- intersect(id_ot_bl, id_shlt_bl) # 8629
length(unique(id_ot_bl))

filter_ot_bl <- filter_iyes %>%
  filter(id %in% id_ot_bl)
length(unique(filter_ot_bl$id)) # 8629

# Keep participants with at least one-wave complete data on outcomes over follow-ups
id_2obs <- filter_ot_bl %>%
  group_by(id) %>%
  filter(n() >= 2) %>%
  dplyr::slice(1) %>%
  ungroup() %>%
  pull(id)

filter_2obs <- filter_ot_bl %>%
  filter(id %in% id_2obs)
length(unique(filter_2obs$id)) # 8136

## Depressive symptoms
id_cesd <- filter_2obs %>%
  rowwise() %>%
  mutate(
    cesd_miss = sum(is.na(c(depres, flone, effort, sleepr, whappy, fsad, going, enlife)), na.rm = F)
  ) %>%
  ungroup() %>%
  mutate(
    with_cesd = ifelse(cesd_miss == 0, 1, 0)
  ) %>%
  group_by(id) %>%
  slice(2:n()) %>%
  mutate(
    t_with_cesd = cumsum(with_cesd)
    ) %>%
  slice(n()) %>%
  filter(t_with_cesd >= 1) %>% 
  ungroup() %>%
  pull(id)

## Self-rated health
id_shlt <- filter_2obs %>%
  mutate(
    with_shlt = ifelse(!is.na(shlt), 1, 0)
  ) %>%
  group_by(id) %>%
  slice(2:n()) %>%
  mutate(
    t_with_shlt = cumsum(with_shlt)
    ) %>%
  slice(n()) %>%
  filter(t_with_shlt >= 1) %>% 
  ungroup() %>%
  pull(id)

## Life satisfaction
id_satlife <- filter_2obs %>%
  mutate(
    with_satlife = ifelse(!is.na(satlife), 1, 0)
  ) %>%
  group_by(id) %>%
  slice(2:n()) %>%
  mutate(
    t_with_satlife = cumsum(with_satlife)
    ) %>%
  slice(n()) %>%
  filter(t_with_satlife >= 1) %>% 
  ungroup() %>%
  pull(id)

id_ot <- intersect(id_cesd, id_satlife) # 6782
length(unique(id_ot))
id_ot <- intersect(id_ot, id_shlt) # 6775
length(unique(id_ot))

filter_ot <- filter_2obs %>%
  filter(id %in% id_ot)
length(unique(filter_ot$id)) # 6775

# Keep participants without dementia and psychological diseases at baseline
id_mental <- filter_ot %>%
  group_by(id) %>%
  slice(1) %>%
  ungroup() %>%
  filter(parkine == "yes" | alzhe == "yes" | psyche == "yes") %>%
  pull(id)

filter_nomental <- filter_ot %>%
  filter(!id %in% id_mental) 
length(unique(filter_nomental$id)) # 5529

# Keep participants with complete data on covariates at baseline
id_cov <- filter_nomental %>%
  rowwise() %>%
  mutate(
    cov_miss = sum(is.na(c(age, male, atotb, lowedu, lbrf, nonmarried, hhres, contact, smoken, weekdrink, phyinact, dis, adl_any, iadl)), na.rm = F)
  ) %>%
  ungroup() %>%
  mutate(
    with_cov = ifelse(cov_miss == 0, 1, 0)
  ) %>%
  group_by(id) %>%
  slice(1) %>%
  ungroup() %>%
  filter(with_cov == 1) %>%
  pull(id)

filter_cov <- filter_ot %>%
  filter(id %in% id_cov) %>%
  rowwise() %>%
  mutate(
    cesd = sum(c(depres, flone, effort, sleepr, whappy, fsad, going, enlife), na.rm = F)
  ) %>%
  ungroup()
length(unique(filter_cov$id)) # 4174

table(filter_cov %>% group_by(id) %>% summarise(count = n()) %>% pull(count))

# Final
bl <- filter_cov %>% 
  group_by(id) %>% 
  slice(1) %>%
  ungroup() %>%
  mutate(
    .keep = "none",
    id, internet_yes, 
    age, male, lowedu, lowwealth = factor(reverse_code(ntile(atotb, 4))), lbrf, 
    nonmarried, hhres, contact, smoken, weekdrink, phyinact,
    dis, adl_any, iadl
    )

final <- filter_cov %>%
  group_by(id) %>%
  mutate(
    fisrt = first(wave),
    cwave = wave - fisrt
  ) %>%
  ungroup() %>%
  mutate(
    .keep = "none",
    id, country, iwy, iwm, wave,
    cesd, shlt, satlife, 
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife),
    depression = ifelse(cesd >= 4, 1, 0), cwave
  ) %>%
  dplyr::select(
    id, country, iwy, iwm, wave,
    cesd, shlt, satlife,
    cesd_stand, shlt_stand, satlife_stand,
    depression, cwave
  )

final_iyes_elsi <- final %>% 
  left_join(., bl, by = "id") %>%
  mutate(
    id = str_c("elsi_", id)
  )

```

### Inverse probability weighting

```{r}

# All observations of all participants in the original data (baseline covariates + time-varying outcomes)
attr_ipw <- tidy_elsi %>% 
  group_by(id) %>% 
  mutate(
    attrition = ifelse(n() == 2, 0, 1)
  ) %>%
  slice(1) %>%
  ungroup() %>%
  select(
    id, wave, internet_yes, 
    age, male, lowedu, atotb, lbrf, 
    nonmarried, hhres, contact, smoken, weekdrink, phyinact,
    dis, adl_any, iadl,
    depres, flone, effort, sleepr, whappy, fsad, going, enlife,
    satlife, shlt,
    attrition
  ) 

      
# Multiple imputation
predictorMatrix <- matrix(0, nrow = dim(attr_ipw)[2], ncol = dim(attr_ipw)[2])
colnames(predictorMatrix) <- colnames(attr_ipw)
rownames(predictorMatrix) <- colnames(attr_ipw)
row_pre <- which(rownames(predictorMatrix) %in% colnames(attr_ipw)[-c(1:2)])
col_pre <- which(colnames(predictorMatrix) %in% colnames(attr_ipw)[-c(1:2)])
predictorMatrix[row_pre, col_pre] <- 1
for(i in 3:dim(attr_ipw)[2]){ predictorMatrix[i,i]<-0 }

cores <- detectCores()
tic()
mi_attr_ipw <- attr_ipw %>%
  futuremice(data = ., m = 10, maxit = 5, predictorMatrix = predictorMatrix, parallelseed = 12345, n.core = cores - 1)
toc() # 40 s


attr_ipw <- attr_ipw %>%
  mutate(
    propensity1 = NA, propensity2 = NA, propensity3 = NA, propensity4 = NA, 
    propensity5 = NA, propensity6 = NA, propensity7 = NA, propensity8 = NA, 
    propensity9 = NA, propensity10 = NA   
  )

# Calculate the probability of included in the analysis using five imputed datasets
tic()
for(i in 1:10){
  mi_data <- mice::complete(mi_attr_ipw, i) %>%
    rowwise() %>%
    mutate(
      .keep = "unused",
      cesd = sum(c(depres, flone, effort, sleepr, whappy, fsad, going, enlife), na.rm = F)
    ) %>%
    ungroup() %>%
    mutate(
      lowwealth = factor(reverse_code(ntile(atotb, 3)))
      )

  attr_weight <- glm(attrition ~ internet_yes + age + male + lowedu + lowwealth + lbrf + 
                        nonmarried + hhres + contact + smoken + weekdrink + phyinact + 
                        dis + adl_any + iadl, 
                      data = mi_data, family = binomial(link = "logit"))
  
  attr_ipw[, paste0("propensity", i)] <- attr_weight$fitted.values

  rm(mi_data, attr_weight)
}
toc()


# Combine weights
attr_ipw <- attr_ipw %>%
  rowwise() %>%
  mutate(
    propensity = mean(c_across(propensity1:propensity10)),
    attrition_ipw = (attrition / propensity) + ((1 - attrition) / (1 - propensity))
  ) %>%
  ungroup() %>%
  mutate(
    id = str_c("elsi_", id)
  )

final_iyes_elsi <- final_iyes_elsi %>%
  left_join(., attr_ipw %>% select(id, attrition_ipw), by = "id")

```

### Internet use and incident depression

```{r}

length(unique(final_iyes_elsi$id)) # 4174

# Keep participants without depression at baseline
final_iyes_inc <- final_iyes_elsi %>%
  group_by(id) %>%
  filter(first(depression == 0)) %>%
  mutate(
    has_depression = any(depression == 1, na.rm = T)
  ) %>%
  ungroup()
length(unique(final_iyes_inc$id)) # 3002

# Date of baseline
final_iyes_inc_bl <- final_iyes_inc %>%
  group_by(id) %>%
  slice(1) %>%
  ungroup() %>%
  mutate(
    iwy_bl = iwy, iwm_bl = iwm
  )

# Date of the first occurrence of depression
final_iyes_inc_dep <- final_iyes_inc %>%
  filter(has_depression == T) %>%
  filter(depression == 1) %>%
  group_by(id) %>%
  slice(1) %>%
  ungroup()

# Date of the last observation
final_iyes_inc_nodep <- final_iyes_inc %>%
  filter(has_depression == F) %>%
  group_by(id) %>%
  slice(n()) %>%
  ungroup()

# Final dataset
final_iyes_inc_elsi <- bind_rows(final_iyes_inc_dep, final_iyes_inc_nodep) %>%
  left_join(final_iyes_inc_bl %>% select(id, iwy_bl, iwm_bl), by = "id") %>%
  rowwise() %>%
  mutate(
    cmonth = iwy*12 + iwm - iwy_bl*12 - iwm_bl
  ) %>%
  ungroup()

rm(final_iyes_inc, final_iyes_inc_bl, final_iyes_inc_dep, final_iyes_inc_nodep)

```


### Supplementary Table 5: compare baseline characteristic between analytic samples and whole samples

```{r}

all <- tidy_elsi %>%
  group_by(id) %>%
  slice(1) %>%
  ungroup() %>%
  mutate(
    .keep = "none",
    internet_yes, 
    age, male, lowedu, atotb, lbrf, 
    nonmarried, hhres, contact, smoken, weekdrink, phyinact,
    dis, adl_any, iadl, sample = "original"
  )

analytic <- filter_cov %>%
  group_by(id) %>%
  slice(1) %>%
  ungroup() %>%
  mutate(
    .keep = "none",
    internet_yes, 
    age, male, lowedu, atotb, lbrf, 
    nonmarried, hhres, contact, smoken, weekdrink, phyinact,
    dis, adl_any, iadl, sample = "analytic"
  )

data <- bind_rows(all, analytic)

var_need <- c("internet_yes", "age", "male", "lowedu", "atotb", "lbrf", "nonmarried", "hhres", "contact", "smoken", "weekdrink", "phyinact", "dis", "adl_any", "iadl")

var_name <- c(
  "Internet use",
  
  "Age (years)",
  "Male",
  "Education",
  "Wealth",
  "Labor force status",

  "Unmarried",  
  "Household size",
  "Weekly contact with other people",
  "Current smoker",
  "Weekly alcohol use",
  "Physical inactivity",
  
  "Number of chronic conditions",
  "ADL disability", 
  "IADL"
)

label_list <- list()
for (i in 1:length(var_name)) {
  formula_str <- paste0(var_need[i], " ~ ", "\"", gsub("'", "'", var_name[i]), "\"")
  label_list[[i]] <- as.formula(formula_str)
}

tbl <- data %>%
  mutate(
    male = relevel(factor(male, labels = c("no", "yes")), ref = "no"),
    lowedu = factor(lowedu, levels = c("primary", "secondary", "tertiary"), labels = c("Primary", "Secondary", "Tertiary")),
    # lowwealth = factor(lowwealth, levels = c("3", "2", "1"), labels = c("Low", "Middle", "High")),
    lbrf = factor(lbrf, levels = c("employed", "retired", "others"), labels = c("Working", "Retired", "Others"))
  ) %>%
  tbl_summary(
    by = sample,
    statistic = list(
      all_continuous() ~ "{mean} ({sd})",
      atotb ~ "{median} ({p25}, {p75})",
      all_categorical() ~ "{n} ({p}%)"
    ),
    label = label_list,
    type = list(dis ~ "continuous", iadl ~ "continuous"),
    digits = list(all_continuous() ~ 1, all_categorical() ~ c(0, 1)),
    missing = "no"
    ) %>%
  add_p(pvalue_fun = function(x) style_pvalue(x, digits = 3))

tbl %>%
  as_flex_table() %>%
  flextable::save_as_docx(path = str_c(getwd(), "/results/Table/Supplementary Table 5_Differences in baseline characteristics between analytic and whole samples_ELSI.docx"))


table <- table(data$sample, data$male)
chisq.test(table, correct = F)

wilcox.test(
  data %>% filter(sample=="original") %>% pull(age),
  data %>% filter(sample=="analytic") %>% pull(age),
  exact = F)

rm(bl, final)
rm(list = ls()[str_detect(string = ls(), pattern = "id_")])
rm(list = ls()[str_detect(string = ls(), pattern = "filter_")])

```

## Bidirectional association: mental health and Internet use

```{r}

# Keep participants aged >=50 years 
id_50plus <- tidy_elsi %>%
  group_by(id) %>%
  slice(1) %>%
  ungroup() %>%
  filter(age >= 50) %>%
  pull(id)

filter_50plus <- tidy_elsi %>%
  filter(id %in% id_50plus)
length(unique(filter_50plus$id)) # 9949

# Keep participants with complete data on internet use at baseline
id_iyes_bl <- filter_50plus %>%
  group_by(id) %>%
  slice(1) %>%
  ungroup() %>%
  filter(!is.na(internet_yes)) %>%
  pull(id)

filter_iyes_bl <- filter_50plus %>%
  filter(id %in% id_iyes_bl)
length(unique(filter_iyes_bl$id)) # 9945

# Keep participants with complete data on outcomes at baseline
## Depressive symptoms
id_cesd_bl <- filter_iyes_bl %>%
  rowwise() %>%
  mutate(
    cesd_miss = sum(is.na(c(depres, flone, effort, sleepr, whappy, fsad, going, enlife)), na.rm = F)
  ) %>%
  ungroup() %>%
  mutate(
    with_cesd = ifelse(cesd_miss == 0, 1, 0)
  ) %>%
  group_by(id) %>%
  slice(1) %>%
  filter(with_cesd == 1) %>% 
  ungroup() %>%
  pull(id)

## Self-rated health
id_shlt_bl <- filter_iyes_bl %>%
  mutate(
    with_shlt = ifelse(!is.na(shlt), 1, 0)
  ) %>%
  group_by(id) %>%
  slice(1) %>%
  filter(with_shlt == 1) %>% 
  ungroup() %>%
  pull(id)

## Life satisfaction
id_satlife_bl <- filter_iyes_bl %>%
  mutate(
    with_satlife = ifelse(!is.na(satlife), 1, 0)
  ) %>%
  group_by(id) %>%
  slice(1) %>%
  filter(with_satlife == 1) %>% 
  ungroup() %>%
  pull(id)

id_ot_bl <- intersect(id_cesd_bl, id_satlife_bl) # 8649
length(unique(id_ot_bl))
id_ot_bl <- intersect(id_ot_bl, id_shlt_bl) # 8629
length(unique(id_ot_bl))

filter_ot_bl <- filter_iyes_bl %>%
  filter(id %in% id_ot_bl)
length(unique(filter_ot_bl$id)) # 8629

# Keep participants with at least one-wave complete data on internet use over follow-ups
id_2obs <- filter_ot_bl %>%
  group_by(id) %>%
  filter(n() >= 2) %>%
  dplyr::slice(1) %>%
  ungroup() %>%
  pull(id)

filter_2obs <- filter_ot_bl %>%
  filter(id %in% id_2obs)
length(unique(filter_2obs$id)) # 8136

id_iyes <- filter_2obs %>%
  mutate(
    with_iyes = ifelse(!is.na(internet_yes), 1, 0)
  ) %>%
  group_by(id) %>%
  slice(2:n()) %>%
  mutate(
    t_with_iyes = cumsum(with_iyes)
    ) %>%
  slice(n()) %>%
  filter(t_with_iyes >= 1) %>% 
  ungroup() %>%
  pull(id)

filter_iyes <- filter_2obs %>%
  filter(id %in% id_iyes)
length(unique(filter_iyes$id)) # 8074

# Keep participants without dementia and psychological diseases at baseline
id_mental <- filter_iyes %>%
  group_by(id) %>%
  slice(1) %>%
  ungroup() %>%
  filter(parkine == "yes" | alzhe == "yes" | psyche == "yes") %>%
  pull(id)

filter_nomental <- filter_iyes %>%
  filter(!id %in% id_mental) 
length(unique(filter_nomental$id)) # 6589

# Keep participants with complete data on covariates at baseline
id_cov <- filter_nomental %>%
  rowwise() %>%
  mutate(
    cov_miss = sum(is.na(c(age, male, atotb, lowedu, lbrf, nonmarried, hhres, contact, smoken, weekdrink, phyinact, dis, adl_any, iadl)), na.rm = F)
  ) %>%
  ungroup() %>%
  mutate(
    with_cov = ifelse(cov_miss == 0, 1, 0)
  ) %>%
  group_by(id) %>%
  slice(1) %>%
  ungroup() %>%
  filter(with_cov == 1) %>%
  pull(id)

filter_cov <- filter_nomental %>%
  filter(id %in% id_cov) %>%
  rowwise() %>%
  mutate(
    cesd = sum(c(depres, flone, effort, sleepr, whappy, fsad, going, enlife), na.rm = F)
  ) %>%
  ungroup()
length(unique(filter_cov$id)) # 4984

table(filter_cov %>% group_by(id) %>% summarise(count = n()) %>% pull(count))

# Final dataset
## Replace with the baseline values
bl <- filter_cov %>% 
  group_by(id) %>% 
  slice(1) %>%
  ungroup() %>%
  mutate(
    .keep = "none",
    id, cesd, satlife, shlt,
    cesd_stand = scale(cesd), satlife_stand = scale(satlife), shlt_stand = scale(shlt), 
    age, male, lowedu, lowwealth = factor(reverse_code(ntile(atotb, 3))), lbrf, 
    nonmarried, hhres, contact, smoken, weekdrink, phyinact,
    dis, adl_any, iadl
    )

final <- filter_cov %>%
  group_by(id) %>%
  mutate(
    fisrt = first(wave),
    cwave = wave - fisrt
  ) %>%
  ungroup() %>%
  dplyr::select(
    id, country, iwy, iwm, wave,
    internet_yes, cwave
  )

final_bidirec_elsi <- final %>% 
  left_join(., bl, by = "id") %>%
  mutate(
    id = str_c("elsi_", id)
  )

rm(bl, final)
rm(list = ls()[str_detect(string = ls(), pattern = "id_")])
rm(list = ls()[str_detect(string = ls(), pattern = "filter_")])

```



# Subgroup analyses: Internet use (yes/no)

## By age

```{r}

# 50-64 years
middle_iyes_elsi <- final_iyes_elsi %>%
  filter(age < 65) %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

# ≥65 years
old_iyes_elsi <- final_iyes_elsi %>%
  filter(age >= 65) %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

```

## By gender

```{r}

# Male
male_iyes_elsi <- final_iyes_elsi %>%
  filter(male == "male") %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

# Female
female_iyes_elsi <- final_iyes_elsi %>%
  filter(male == "female") %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

```

## By marital status

```{r}

# Married
married_iyes_elsi <- final_iyes_elsi %>%
  filter(nonmarried == "no") %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

# Unmarried
nonmarried_iyes_elsi <- final_iyes_elsi %>%
  filter(nonmarried == "yes") %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

```

## By weekly contact

```{r}

# Weekly contact with other people
contact_iyes_elsi <- final_iyes_elsi %>%
  filter(contact == "yes") %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

# No weekly contact
nocontact_iyes_elsi <- final_iyes_elsi %>%
  filter(contact == "no") %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

```


## By education

```{r}

# Primary
pedu_iyes_elsi <- final_iyes_elsi %>%
  filter(lowedu == "primary") %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

# Secondary
sedu_iyes_elsi <- final_iyes_elsi %>%
  filter(lowedu == "secondary") %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

# Tertiary
tedu_iyes_elsi <- final_iyes_elsi %>%
  filter(lowedu == "tertiary") %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

```

## By household wealth

```{r}

# Low
lwealth_iyes_elsi <- final_iyes_elsi %>%
  filter(lowwealth == 3) %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

# Middle
mwealth_iyes_elsi <- final_iyes_elsi %>%
  filter(lowwealth == 2) %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

# High
hwealth_iyes_elsi <- final_iyes_elsi %>%
  filter(lowwealth == 1) %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

```

## By labor force status

```{r}

# Working
work_iyes_elsi <- final_iyes_elsi %>%
  filter(lbrf == "employed") %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

# Retired
retired_iyes_elsi <- final_iyes_elsi %>%
  filter(lbrf == "retired") %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

# Others
others_iyes_elsi <- final_iyes_elsi %>%
  filter(lbrf == "others") %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

```

## By current smoking 

```{r}

# Current smoking
smoke_iyes_elsi <- final_iyes_elsi %>%
  filter(smoken == "yes") %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

# No smoking
nosmoke_iyes_elsi <- final_iyes_elsi %>%
  filter(smoken == "no") %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

```

## By alcohol consumption

```{r}

# Weekly alcohol use
drink_iyes_elsi <- final_iyes_elsi %>%
  filter(weekdrink == "yes") %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

# Less than weekly alcohol use
nodrink_iyes_elsi <- final_iyes_elsi %>%
  filter(weekdrink == "no") %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )


```

## By physical activity

```{r}

# Physical inactivity
phyinact_iyes_elsi <- final_iyes_elsi %>%
  filter(phyinact == "yes") %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

# Physical activity
phyact_iyes_elsi <- final_iyes_elsi %>%
  filter(phyinact == "no") %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

```

## By ADL disability

```{r}

# ADL disability
adl_iyes_elsi <- final_iyes_elsi %>%
  filter(adl_any == "yes") %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

# No ADL limitation
noadl_iyes_elsi <- final_iyes_elsi %>%
  filter(adl_any == "no") %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

```

## By chronic conditions

```{r}

# ≥1 chronic conditions
dis_iyes_elsi <- final_iyes_elsi %>%
  filter(dis > 0) %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

# No chronic conditions
nodis_iyes_elsi <- final_iyes_elsi %>%
  filter(dis == 0) %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

```


# Sentivity analyses: Multiple imputation

## Internet use (yes/no)

```{r}

# There is no missing value in this dataset

```

# Save data

```{r}

save(
  final_iyes_elsi, final_iyes_inc_elsi, final_bidirec_elsi,# Complete cases
  middle_iyes_elsi, old_iyes_elsi, male_iyes_elsi, female_iyes_elsi,
  married_iyes_elsi, nonmarried_iyes_elsi, contact_iyes_elsi, nocontact_iyes_elsi,
  pedu_iyes_elsi, sedu_iyes_elsi, tedu_iyes_elsi,
  lwealth_iyes_elsi, mwealth_iyes_elsi, hwealth_iyes_elsi,
  work_iyes_elsi, retired_iyes_elsi, others_iyes_elsi,
  smoke_iyes_elsi, nosmoke_iyes_elsi, drink_iyes_elsi, nodrink_iyes_elsi,
  phyinact_iyes_elsi, phyact_iyes_elsi, adl_iyes_elsi, noadl_iyes_elsi,
  dis_iyes_elsi, nodis_iyes_elsi, # Subgroup analyses
  file = str_c(getwd(), "/data/processed/elsi_processed_data.RData", sep = "")
  )

```
