---
title: "Internet use and mental health"
author: "Yan Luo"
date: '2023-10-01'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Make sure the working directory is "your path/internet-use-mental-health"
knitr::opts_knit$set(root.dir = "D:/github_project/internet-use-mental-health")

library(tidyverse)
library(haven)
library(mice)
library(tictoc)
library(doParallel)

```

# Self-constructed functions

```{r}

reverse_code <- function(x) {
  max_val <- max(x, na.rm = T)
  return(max_val - x + 1)
}

```

# Import data

## Main datasets: Harmonized_HRS and RAND_HRS

```{r}

print(getwd())

# Import the data
memory.limit(size = 18000)
harm_hrs <- read_sas(str_c(getwd(), "/data/raw/hrs/H_HRS_c.sas7bdat", sep = ""))
rand_hrs <- read_sas(str_c(getwd(), "/data/raw/hrs/randhrs1992_2018v2.sas7bdat", sep = ""))

## Transform Harmonized_HRS from wide format to long format
rand_hrs_age <- rand_hrs %>%
  dplyr::select(
    c(HHIDPN) | (starts_with("R") & contains("AGE") & ends_with("_E") & !contains("ESP")) # Age
  ) %>% 
  rename_with(tolower)

wide_harm_hrs <- harm_hrs %>%
  left_join(rand_hrs_age, by = "hhidpn") %>%
  dplyr::select(
    c(hhid, pn, hhidpn, raeducl) | # ID, education
      (starts_with("r") & contains("age") & ends_with("_e")) | # Age
      (starts_with("r") & ends_with("satlife")) # Life satisfaction
     ) %>% 
  mutate( # generate n variables (with NA values or values from other related variables) to make the number of measurements equal to 14 (R1 to R14)
    .keep = "unused",
    r1satlife = NA, r2satlife = NA, r3satlife = NA, r4satlife = NA, r5satlife = NA, r6satlife = NA, r7satlife = NA, r8satlife = NA
  ) 

index_reorder <- str_detect(names(wide_harm_hrs), "[h-r][0-9]+(.*)")
names_reorder <- names(wide_harm_hrs)[index_reorder] %>% 
  str_match("[h-r]([0-9]+)(.*)") %>% 
  as_tibble() %>% 
  arrange(.[[3]], as.numeric(.[[2]])) %>%
  dplyr::select(V1) %>%
  as_vector("character") %>% unname()

long_harm_hrs <- wide_harm_hrs %>% 
  dplyr::select(!contains(names_reorder), contains(names_reorder)) %>%
  pivot_longer(
    col = !c(hhid, pn, hhidpn, raeducl),
    names_to = ".value",
    names_pattern = "[h-r][0-9]+(.*)"
  )

rm(harm_hrs, wide_harm_hrs, rand_hrs_age)

## Transform RAND_HRS from wide format to long format
wide_rand_hrs <- rand_hrs %>%
  dplyr::select(
    c(HHIDPN, HHID, PN, RAGENDER) | 
      (starts_with("INW")) | # Response Indicator
      (starts_with("R") & (ends_with("IWEND") | ends_with("IWENDY") | ends_with("IWENDM"))) | # Interview dates
      (starts_with("R") & contains("AGE") & ends_with("_E") & !contains("ESP")) | # Age
      (starts_with("H") & ends_with("ATOTB")) | # Household wealth
      (starts_with("R") & (ends_with("LBRF"))) | # Labor force status
      (starts_with("H") & ends_with("HHRES")) | # Household size
      (starts_with("R") & (ends_with("SMOKEV") | ends_with("SMOKEN") | ends_with("DRINKD") | ends_with("VGACTX") | ends_with("MDACTX"))) | # Health behaviors
      (starts_with("R") & (ends_with("MSTAT"))) | # Marital status
      (starts_with("R") & (ends_with("HIBPE") | ends_with("DIABE") | ends_with("CANCRE") | ends_with("LUNGE") | ends_with("HEARTE") | ends_with("STROKE") | ends_with("PSYCHE") | ends_with("ARTHRE"))) | # Chronic diseases
      (starts_with("R") & (ends_with("MEMRYE") | ends_with("ALZHEE") | ends_with("DEMENE"))) | # Memory-related diseases, Alzheimer’s disease, dementia
      (starts_with("R") & (ends_with("BATHA") | ends_with("EATA") | ends_with("BEDA") | ends_with("TOILTA") | ends_with("WALKRA") | ends_with("DRESSA"))) | # ADL
      (starts_with("R") & (ends_with("MAPA") | ends_with("PHONEA") | ends_with("MONEYA") | ends_with("MEDSA") | ends_with("SHOPA") | ends_with("MEALSA"))) | # IADL
      (starts_with("R") & (ends_with("DEPRES") | ends_with("EFFORT") | ends_with("SLEEPR") | ends_with("WHAPPY") | ends_with("FLONE") | ends_with("FSAD") | ends_with("GOING") | ends_with("ENLIFE") | ends_with("CESD") | ends_with("CESDM"))) | # CES-D
      (starts_with("R") & ends_with("SHLT")) # Self-reported Health
     ) %>% 
  mutate(
    .keep = "unused",
    # Memory-related diseases, Alzheimer’s disease, dementia
    R1MEMRYE = NA, R2MEMRYE = NA, R3MEMRYE = NA, 
    R10MEMRYE = R10ALZHEE + R10DEMENE, R11MEMRYE = R11ALZHEE + R11DEMENE, R12MEMRYE = R12ALZHEE + R12DEMENE, R13MEMRYE = R13ALZHEE + R13DEMENE, R14MEMRYE = R14ALZHEE + R14DEMENE,
    # ADL
    R1BATHA = NA, R1EATA = NA, R1BEDA = NA, R1TOILTA = NA, R1WALKRA = NA, R1DRESSA = NA,
    # IADL
    R1MAPA = NA, R1PHONEA = NA, R1MONEYA = NA, R1MEDSA = NA, R1SHOPA = NA, R1MEALSA = NA,
    # Drinking
    R1DRINKD = NA, R2DRINKD = NA,
    # Physical activity
    R1VGACTX = NA, R2VGACTX = NA, R3VGACTX = NA, R4VGACTX = NA, R5VGACTX = NA, R6VGACTX = NA, R1MDACTX = NA, R2MDACTX = NA, R3MDACTX = NA, R4MDACTX = NA, R5MDACTX = NA, R6MDACTX = NA,
    # CES-D
    R1DEPRES = NA, R1EFFORT = NA, R1SLEEPR = NA, R1WHAPPY = NA, R1FLONE = NA, R1FSAD = NA, R1GOING = NA, R1ENLIFE = NA, R1CESD = NA
  ) %>%
  dplyr::select(!c(REIWEND, REMSTAT))

index_reorder <- str_detect(names(wide_rand_hrs), "[H-R][0-9]+(.*)")
names_reorder <- names(wide_rand_hrs)[index_reorder] %>% 
  str_match("[H-R]([0-9]+)(.*)") %>% 
  as_tibble() %>% 
  arrange(.[[3]], as.numeric(.[[2]])) %>%
  dplyr::select(V1) %>%
  as_vector("character") %>% 
  unname()

long_rand_hrs <- wide_rand_hrs %>% 
  dplyr::select(!contains(names_reorder), contains(names_reorder)) %>%
  dplyr::select(!c(INW1, INW2, INW3, INW4, INW5, INW6, INW7, INW8, INW9, INW10, INW11, INW12, INW13, INW14)) %>%
  pivot_longer(
    col = !c(HHIDPN, HHID, PN, RAGENDER),
    names_to = ".value", 
    names_pattern = "[H-R][0-9]+(.*)"
  ) %>%
  group_by(HHIDPN) %>%
  mutate(
    followup = row_number(),
    wave = case_when( # the mean value of the interview year for all participants at each wave
      IWENDY %in% c(1993:1995) ~ 1994,
      IWENDY %in% c(1995:1997) ~ 1996,
      IWENDY %in% c(1998:1999) ~ 1998,
      IWENDY %in% c(2000) ~ 2000,
      IWENDY %in% c(2002:2003) ~ 2002,
      IWENDY %in% c(2004:2005) ~ 2004,
      IWENDY %in% c(2006:2007) ~ 2006,
      IWENDY %in% c(2008:2009) ~ 2008,
      IWENDY %in% c(2010:2011) ~ 2010,
      IWENDY %in% c(2012:2013) ~ 2012,
      IWENDY %in% c(2014:2015) ~ 2014,
      IWENDY %in% c(2016:2017) ~ 2016,
      IWENDY %in% c(2018) & followup < max(row_number()) ~ 2016,
      IWENDY %in% c(2018) & followup == max(row_number()) ~ 2018,
      IWENDY %in% c(2019) ~ 2018
    )
  ) %>%
  ungroup() %>%
  dplyr::select(!c(followup))

rm(rand_hrs, wide_rand_hrs, index_reorder, names_reorder)

```

## 2008 - 2018 cohort core questionnaire

```{r}

# 2008
hrs_core_w9 <- read_dta(str_c(getwd(), "/data/raw/hrs/H08W_R.dta", sep = "")) %>%
  mutate(
    .keep = "none",
    hhidpn = as.numeric(str_c(HHID, PN)), hhid = as.numeric(HHID), subhh = LSUBHH, wave = 2008,
    internet_yes = LW303
  )

# 2010
hrs_core_w10 <- read_dta(str_c(getwd(), "/data/raw/hrs/H10W_R.dta", sep = "")) %>%
  mutate(
    .keep = "none",
    hhidpn = as.numeric(str_c(HHID, PN)), hhid = as.numeric(HHID), subhh = MSUBHH, wave = 2010,
    internet_yes = MW303
  )

# 2012
hrs_core_w11 <- read_dta(str_c(getwd(), "/data/raw/hrs/H12W_R.dta", sep = "")) %>%
  mutate(
    .keep = "none",
    hhidpn = as.numeric(str_c(HHID, PN)), hhid = as.numeric(HHID), subhh = NSUBHH, wave = 2012,
    internet_yes = NW303
  )

# 2014
hrs_core_w12 <- read_dta(str_c(getwd(), "/data/raw/hrs/H14W_R.dta", sep = "")) %>%
  mutate(
    .keep = "none",
    hhidpn = as.numeric(str_c(HHID, PN)), hhid = as.numeric(HHID), subhh = OSUBHH, wave = 2014,
    internet_yes = OW303
  )

# 2016
hrs_core_w13 <- read_dta(str_c(getwd(), "/data/raw/hrs/H16W_R.dta", sep = "")) %>%
  mutate(
    .keep = "none",
    hhidpn = as.numeric(str_c(HHID, PN)), hhid = as.numeric(HHID), subhh = PSUBHH, wave = 2016,
    internet_yes = PW303
  )

# 2018
hrs_core_w14 <- read_dta(str_c(getwd(), "/data/raw/hrs/H18W_R.dta", sep = "")) %>%
  mutate(
    .keep = "none",
    hhidpn = as.numeric(str_c(HHID, PN)), hhid = as.numeric(HHID), subhh = QSUBHH, wave = 2018,
    internet_yes = QW303
  )

```

## 2008 - 2018 cohort LBQ questionnaire

```{r}

# 2008 
hrs_lbq_w9 <- read_dta(str_c(getwd(), "/data/raw/hrs/H08LB_R.dta", sep = "")) %>%
  mutate(
    .keep = "none",
    hhidpn = as.numeric(str_c(HHID, PN)), wave = 2008, 
    lbelig = LLBELIG, lbcomp = LLBCOMP, 
    internet_freq = LLB001l
  )

# 2010 
hrs_lbq_w10 <- read_dta(str_c(getwd(), "/data/raw/hrs/H10LB_R.dta", sep = "")) %>%
  mutate(
    .keep = "none",
    hhidpn = as.numeric(str_c(HHID, PN)), wave = 2010, 
    lbelig = MLBELIG, lbcomp = MLBCOMP,
    internet_freq = MLB001N
  )

# 2012
hrs_lbq_w11 <- read_dta(str_c(getwd(), "/data/raw/hrs/H12LB_R.dta", sep = "")) %>%
  mutate(
    .keep = "none",
    hhidpn = as.numeric(str_c(HHID, PN)), wave = 2012, 
    lbelig = NLBELIG, lbcomp = NLBCOMP,
    internet_freq = NLB001N
  )

# 2014 
hrs_lbq_w12 <- read_dta(str_c(getwd(), "/data/raw/hrs/H14LB_R.dta", sep = "")) %>%
  mutate(
    .keep = "none",
    hhidpn = as.numeric(str_c(HHID, PN)), wave = 2014, 
    lbelig = OLBELIG, lbcomp = OLBCOMP,
    internet_freq = OLB001N
  )

# 2016 
hrs_lbq_w13 <- read_dta(str_c(getwd(), "/data/raw/hrs/H16LB_R.dta", sep = "")) %>%
  mutate(
    .keep = "none",
    hhidpn = as.numeric(str_c(HHID, PN)), wave = 2016, 
    lbelig = PLBELIG, lbcomp = PLBCOMP,
    internet_freq = PLB001N
  )

# 2018 
hrs_lbq_w14 <- read_dta(str_c(getwd(), "/data/raw/hrs/H18LB_R.dta", sep = "")) %>%
  mutate(
    .keep = "none",
    hhidpn = as.numeric(str_c(HHID, PN)), wave = 2018, 
    lbelig = QLBELIG, lbcomp = QLBCOMP,
    internet_freq = QLB001N
  )

```

## Polygenic risk score

```{r}

# African ancestry
hrs_pgs_a <- read_dta(str_c(getwd(), "/data/raw/hrs/pgenscore4a_r.dta", sep = "")) %>%
  mutate(
    .keep = "none",
    hhidpn = as.numeric(str_c(hhid, pn)), depsymp_pgs = A4_DEPSYMP_SSGAC16, 
    wellb_pgs = A4_WELLB_SSGAC16
    )

# European ancestry
hrs_pgs_e <- read_dta(str_c(getwd(), "/data/raw/hrs/pgenscore4e_r.dta", sep = "")) %>%
  mutate(
    .keep = "none",
    hhidpn = as.numeric(str_c(hhid, pn)), depsymp_pgs = E4_DEPSYMP_SSGAC16, 
    wellb_pgs = E4_WELLB_SSGAC16
    )

hrs_pgs <- bind_rows(hrs_pgs_a, hrs_pgs_e)
rm(hrs_pgs_a, hrs_pgs_e)

```

# Variable definition

```{r}

# Merge datasets
long_hrs <- bind_cols(long_rand_hrs, long_harm_hrs) %>% 
  dplyr::select(-c(hhid, pn, hhidpn, agem_e, agey_e)) %>%
  rename_with(tolower)
rm(long_rand_hrs, long_harm_hrs)

long_core <- bind_rows(hrs_core_w9, hrs_core_w10, hrs_core_w11, hrs_core_w12, hrs_core_w13, hrs_core_w14)
rm(hrs_core_w9, hrs_core_w10, hrs_core_w11, hrs_core_w12, hrs_core_w13, hrs_core_w14)

long_lbq <- bind_rows(hrs_lbq_w9, hrs_lbq_w10, hrs_lbq_w11, hrs_lbq_w12, hrs_lbq_w13, hrs_lbq_w14)
rm(hrs_lbq_w9, hrs_lbq_w10, hrs_lbq_w11, hrs_lbq_w12, hrs_lbq_w13, hrs_lbq_w14)


# Define variables
tidy_hrs <- long_hrs %>%
  filter(!is.na(iwendy)) %>%
  filter(wave >= 2008) %>% 
  left_join(long_lbq, by = c("hhidpn", "wave")) %>%
  left_join(
    long_core %>% dplyr::select(!c(hhid, subhh)), 
    by = c("hhidpn", "wave")) %>%
  left_join(hrs_pgs, by = "hhidpn") %>%
  mutate(
    .keep = "none",
    ## Basic information
    id = hhidpn, cohort = "hrs", country = 840, wave, 
    iwy = iwendy, iwm = iwendm,
    
    ## Exposure variables 
    internet_yes = case_when(
      internet_yes == 1 ~ "yes",
      internet_yes == 5 ~ "no",
      TRUE ~ NA_character_
    ),
    internet_yes = relevel(factor(internet_yes), ref = "no"),
    internet_freq = case_when(
      internet_freq == 1 ~ "daily",
      internet_freq %in% c(2,3) ~ "weekly",
      internet_freq %in% c(4:6) ~ "notregularly",
      internet_freq == 7 ~ "none",
      TRUE ~ NA_character_
    ),
    internet_freq = factor(internet_freq, levels = c("none", "notregularly", "weekly", "daily")),
    
    ## Outcomes
    # depressive symptom
    depres, flone, effort, sleepr, whappy = 1-whappy, fsad, going, enlife = 1-enlife,
    # self-rated health
    shlt = reverse_code(shlt), 
    # life satisfaction
    satlife,
    
    ## Polygenic risk score
    depsymp_pgs, wellb_pgs,
    
    ## Covariates
    # Demographics
    age = agey_e, 
    male = ifelse(ragender == 2, "female", "male"), male = relevel(factor(male), ref = "female"),
    nonmarried = case_when(
      mstat %in% c(1:3) ~ "no",
      mstat %in% c(4:8) ~ "yes",
      TRUE ~ NA_character_
      ),
    nonmarried = relevel(factor(nonmarried), ref = "no"),
    hhres, 
    
    # Socioeconomic status
    atotb, 
    lowedu = case_when(
      raeducl == 3 ~ "tertiary",
      raeducl == 2 ~ "secondary",
      raeducl == 1 ~ "primary",
      TRUE ~ NA_character_
    ),
    lowedu = relevel(factor(lowedu), ref = "tertiary"),
    lbrf = case_when(
      lbrf %in% c(1,2) ~ "employed",
      lbrf %in% c(4,5) ~ "retired",
      lbrf %in% c(3,6,7) ~ "others",
      TRUE ~ NA_character_
    ), 
    lbrf = relevel(factor(lbrf), ref = "employed"),
    
    # Health behaviors
    smoke = case_when(
      smokev == 0 ~ "never",
      smokev == 1 & smoken == 0 ~ "ever",
      smoken == 1 ~ "current",
      TRUE ~ NA_character_
    ),
    smoke = relevel(factor(smoke), ref = "never"),
    smoken = ifelse(smoken == 1, "yes", "no"), smoken = relevel(factor(smoken), ref = "no"),
    weekdrink = case_when(
      drinkd == 0 ~ "no",
      drinkd >= 1 ~ "yes",
      TRUE ~ NA_character_
    ),
    weekdrink = relevel(factor(weekdrink), ref = "no"),
    phyinact = case_when(
      vgactx %in% c(1:4) | mdactx %in% c(1:4) ~ "no",
      vgactx == 5 & mdactx == 5 ~ "yes",
      TRUE ~ NA_character_
    ),
    phyinact = relevel(factor(phyinact), ref = "no"),
    
    # Physical health
    hibpe, diabe, cancre, lunge, hearte, stroke, arthre, 
    psyche = factor(psyche, labels = c("no", "yes")), 
    psyche = relevel(factor(psyche), ref = "no"),
    memrye = case_when(
      memrye >= 1 ~ 1,
      memrye == 0 ~ 0,
      TRUE ~ NA_real_
      ),
    memrye = factor(memrye, labels = c("no", "yes")), 
    memrye = relevel(factor(memrye), ref = "no"),
    dressa, batha, eata, beda, toilta, walkra,
    moneya, medsa, shopa, mealsa, phonea, mapa
  ) %>%
  arrange(id, wave) %>%
  rowwise() %>%
  mutate(
    dis = sum(c(hibpe, diabe, cancre, lunge, hearte, stroke, arthre), na.rm = T),
    dis_miss = sum(is.na(c(hibpe, diabe, cancre, lunge, hearte, stroke, arthre)), na.rm = F),
    adl = sum(c(dressa, batha, eata, beda, toilta, walkra), na.rm = T),
    adl_miss = sum(is.na(c(dressa, batha, eata, beda, toilta, walkra)), na.rm = F),
    iadl = sum(c(moneya, medsa, shopa, mealsa, phonea), na.rm = T),
    iadl_miss = sum(is.na(c(moneya, medsa, shopa, mealsa, phonea)), na.rm = F),
  ) %>%
  ungroup() %>%
  mutate(
    dis = ifelse(dis_miss == 7, NA, dis),
    adl = ifelse(adl_miss == 6, NA, adl),
    iadl = ifelse(iadl_miss == 5, NA, iadl),
    adl_any = ifelse(adl == 0, "no", "yes"), adl_any = relevel(factor(adl_any), ref = "no")
  )

# The number of participants
length(unique(tidy_hrs$id))

```

# Generate analytic samples

## Internet use (yes/no)

```{r}

# Keep participants aged >=51 years (HRS is designed to recruit adults aged ≥51 years)
id_50plus <- tidy_hrs %>%
  group_by(id) %>%
  slice(1) %>%
  ungroup() %>%
  filter(age >= 51) %>%
  pull(id)

filter_50plus <- tidy_hrs %>%
  filter(id %in% id_50plus)
length(unique(filter_50plus$id)) # 27333

# Keep participants with complete data on internet use at baseline
id_iyes <- filter_50plus %>%
  group_by(id) %>%
  slice(1) %>%
  ungroup() %>%
  filter(!is.na(internet_yes)) %>%
  pull(id)

filter_iyes <- filter_50plus %>%
  filter(id %in% id_iyes)
length(unique(filter_iyes$id)) # 26976

# Keep participants with complete data on outcomes at baseline
## Depressive symptoms
id_cesd_bl <- filter_iyes %>%
  rowwise() %>%
  mutate(
    cesd_miss = sum(is.na(c(depres, flone, effort, sleepr, whappy, fsad, going, enlife)), na.rm = F)
  ) %>%
  ungroup() %>%
  mutate(
    with_cesd = ifelse(cesd_miss == 0, 1, 0)
  ) %>%
  group_by(id) %>%
  slice(1) %>%
  filter(with_cesd == 1) %>% 
  ungroup() %>%
  pull(id)

## Self-rated health
id_shlt_bl <- filter_iyes %>%
  mutate(
    with_shlt = ifelse(!is.na(shlt), 1, 0)
  ) %>%
  group_by(id) %>%
  slice(1) %>%
  filter(with_shlt == 1) %>% 
  ungroup() %>%
  pull(id)

## Life satisfaction
id_satlife_bl <- filter_iyes %>%
  mutate(
    with_satlife = ifelse(!is.na(satlife), 1, 0)
  ) %>%
  group_by(id) %>%
  slice(1) %>%
  filter(with_satlife == 1) %>% 
  ungroup() %>%
  pull(id)

id_ot_bl <- intersect(id_cesd_bl, id_shlt_bl) # 25248
id_ot_bl <- intersect(id_ot_bl, id_satlife_bl) # 25177

filter_ot_bl <- filter_iyes %>%
  filter(id %in% id_ot_bl)
length(unique(filter_ot_bl$id)) # 25177

# Keep participants with at least one-wave complete data on outcomes over follow-ups
id_2obs <- filter_ot_bl %>%
  group_by(id) %>%
  filter(n() >= 2) %>%
  dplyr::slice(1) %>%
  ungroup() %>%
  pull(id)

filter_2obs <- filter_ot_bl %>%
  filter(id %in% id_2obs)
length(unique(filter_2obs$id)) # 22605

## Depressive symptoms
id_cesd <- filter_2obs %>%
  rowwise() %>%
  mutate(
    cesd_miss = sum(is.na(c(depres, flone, effort, sleepr, whappy, fsad, going, enlife)), na.rm = F)
  ) %>%
  ungroup() %>%
  mutate(
    with_cesd = ifelse(cesd_miss == 0, 1, 0)
  ) %>%
  group_by(id) %>%
  slice(2:n()) %>%
  mutate(
    t_with_cesd = cumsum(with_cesd)
    ) %>%
  slice(n()) %>%
  filter(t_with_cesd >= 1) %>% 
  ungroup() %>%
  pull(id)

## Self-rated health
id_shlt <- filter_2obs %>%
  mutate(
    with_shlt = ifelse(!is.na(shlt), 1, 0)
  ) %>%
  group_by(id) %>%
  slice(2:n()) %>%
  mutate(
    t_with_shlt = cumsum(with_shlt)
    ) %>%
  slice(n()) %>%
  filter(t_with_shlt >= 1) %>% 
  ungroup() %>%
  pull(id)

## Life satisfaction
id_satlife <- filter_2obs %>%
  mutate(
    with_satlife = ifelse(!is.na(satlife), 1, 0)
  ) %>%
  group_by(id) %>%
  slice(2:n()) %>%
  mutate(
    t_with_satlife = cumsum(with_satlife)
    ) %>%
  slice(n()) %>%
  filter(t_with_satlife >= 1) %>% 
  ungroup() %>%
  pull(id)

id_ot <- intersect(id_cesd, id_shlt) # 22039
id_ot <- intersect(id_ot, id_satlife) # 21987

filter_ot <- filter_2obs %>%
  filter(id %in% id_ot)
length(unique(filter_ot$id)) # 21987

# Keep participants without dementia and psychological diseases at baseline
id_mental <- filter_ot %>%
  group_by(id) %>%
  slice(1) %>%
  ungroup() %>%
  filter(memrye == "yes" | psyche == "yes") %>%
  pull(id)

filter_nomental <- filter_ot %>%
  filter(!id %in% id_mental) 
length(unique(filter_nomental$id)) # 18355

# Keep participants with complete data on covariates at baseline
id_cov <- filter_nomental %>%
  rowwise() %>%
  mutate(
    cov_miss = sum(is.na(c(age, male, atotb, lowedu, lbrf, nonmarried, hhres, smoken, weekdrink, phyinact, dis, adl_any, iadl)), na.rm = F)
  ) %>%
  ungroup() %>%
  mutate(
    with_cov = ifelse(cov_miss == 0, 1, 0)
  ) %>%
  group_by(id) %>%
  slice(1) %>%
  ungroup() %>%
  filter(with_cov == 1) %>%
  pull(id)

filter_cov_iyes <- filter_nomental %>%
  filter(id %in% id_cov) %>%
  rowwise() %>%
  mutate(
    cesd = sum(c(depres, flone, effort, sleepr, whappy, fsad, going, enlife), na.rm = F)
  ) %>%
  ungroup()
length(unique(filter_cov_iyes$id)) # 18225

table(filter_cov_iyes %>% group_by(id) %>% summarise(count = n()) %>% pull(count))

# Final dataset
## Replace with the baseline values
bl <- filter_cov_iyes %>% 
  group_by(id) %>% 
  slice(1) %>%
  ungroup() %>%
  mutate(
    .keep = "none",
    id, internet_yes, 
    age, male, lowedu, lowwealth = factor(reverse_code(ntile(atotb, 3))), lbrf, 
    nonmarried, hhres, smoken, weekdrink, phyinact,
    dis, adl_any, iadl
    )

final <- filter_cov_iyes %>%
  group_by(id) %>%
  mutate(
    fisrt = first(wave),
    cwave = wave - fisrt
  ) %>%
  ungroup() %>%
  mutate(
    .keep = "none",
    id, country, iwy, iwm, wave,
    cesd, shlt, satlife, 
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife),
    cwave
  ) %>%
  dplyr::select(
    id, country, iwy, iwm, wave,
    cesd, shlt, satlife,
    cesd_stand, shlt_stand, satlife_stand,
    cwave
  )

final_iyes_hrs <- final %>% 
  left_join(., bl, by = "id") %>%
  mutate(
    id = str_c("hrs_", id)
  )

rm(bl, final)
rm(list = ls()[str_detect(string = ls(), pattern = "id_")])
object <- ls()[str_detect(string = ls(), pattern = "filter_")]
rm(list = object[!object %in% "filter_cov_iyes"])

```

## Internet use frequency

```{r}

# Keep participants aged >=51 years
id_50plus <- tidy_hrs %>%
  group_by(id) %>%
  slice(1) %>%
  ungroup() %>%
  filter(age >= 51) %>%
  pull(id)

filter_50plus <- tidy_hrs %>%
  filter(id %in% id_50plus)
length(unique(filter_50plus$id)) # 27333

# Keep participants with complete data on internet use frequency at baseline
id_ifreq <- filter_50plus %>%
  group_by(id) %>%
  slice(1) %>%
  ungroup() %>%
  filter(!is.na(internet_freq)) %>%
  pull(id)

filter_ifreq <- filter_50plus %>%
  filter(id %in% id_ifreq)
length(unique(filter_ifreq$id)) # 9164

# Keep participants with complete data on outcomes at baseline
## Depressive symptoms
id_cesd_bl <- filter_ifreq %>%
  rowwise() %>%
  mutate(
    cesd_miss = sum(is.na(c(depres, flone, effort, sleepr, whappy, fsad, going, enlife)), na.rm = F)
  ) %>%
  ungroup() %>%
  mutate(
    with_cesd = ifelse(cesd_miss == 0, 1, 0)
  ) %>%
  group_by(id) %>%
  slice(1) %>%
  filter(with_cesd == 1) %>% 
  ungroup() %>%
  pull(id)

## Self-rated health
id_shlt_bl <- filter_ifreq %>%
  mutate(
    with_shlt = ifelse(!is.na(shlt), 1, 0)
  ) %>%
  group_by(id) %>%
  slice(1) %>%
  filter(with_shlt == 1) %>% 
  ungroup() %>%
  pull(id)

## Life satisfaction
id_satlife_bl <- filter_ifreq %>%
  mutate(
    with_satlife = ifelse(!is.na(satlife), 1, 0)
  ) %>%
  group_by(id) %>%
  slice(1) %>%
  filter(with_satlife == 1) %>% 
  ungroup() %>%
  pull(id)

id_ot_bl <- intersect(id_cesd_bl, id_shlt_bl) # 8873
id_ot_bl <- intersect(id_ot_bl, id_satlife_bl) # 8865

filter_ot_bl <- filter_ifreq %>%
  filter(id %in% id_ot_bl)
length(unique(filter_ot_bl$id)) # 8865

# Keep participants with at least one-wave complete data on outcomes over follow-ups
id_2obs <- filter_ot_bl %>%
  group_by(id) %>%
  filter(n() >= 2) %>%
  dplyr::slice(1) %>%
  ungroup() %>%
  pull(id)

filter_2obs <- filter_ot_bl %>%
  filter(id %in% id_2obs)
length(unique(filter_2obs$id)) # 8126

## Depressive symptoms
id_cesd <- filter_2obs %>%
  rowwise() %>%
  mutate(
    cesd_miss = sum(is.na(c(depres, flone, effort, sleepr, whappy, fsad, going, enlife)), na.rm = F)
  ) %>%
  ungroup() %>%
  mutate(
    with_cesd = ifelse(cesd_miss == 0, 1, 0)
  ) %>%
  group_by(id) %>%
  slice(2:n()) %>%
  mutate(
    t_with_cesd = cumsum(with_cesd)
    ) %>%
  slice(n()) %>%
  filter(t_with_cesd >= 1) %>% 
  ungroup() %>%
  pull(id)

## Self-rated health
id_shlt <- filter_2obs %>%
  mutate(
    with_shlt = ifelse(!is.na(shlt), 1, 0)
  ) %>%
  group_by(id) %>%
  slice(2:n()) %>%
  mutate(
    t_with_shlt = cumsum(with_shlt)
    ) %>%
  slice(n()) %>%
  filter(t_with_shlt >= 1) %>% 
  ungroup() %>%
  pull(id)

## Life satisfaction
id_satlife <- filter_2obs %>%
  mutate(
    with_satlife = ifelse(!is.na(satlife), 1, 0)
  ) %>%
  group_by(id) %>%
  slice(2:n()) %>%
  mutate(
    t_with_satlife = cumsum(with_satlife)
    ) %>%
  slice(n()) %>%
  filter(t_with_satlife >= 1) %>% 
  ungroup() %>%
  pull(id)

id_ot <- intersect(id_cesd, id_shlt) # 7960
id_ot <- intersect(id_ot, id_satlife) # 7948

filter_ot <- filter_2obs %>%
  filter(id %in% id_ot)
length(unique(filter_ot$id)) # 7948

# Keep participants without dementia and psychological diseases at baseline
id_mental <- filter_ot %>%
  group_by(id) %>%
  slice(1) %>%
  ungroup() %>%
  filter(memrye == "yes" | psyche == "yes") %>%
  pull(id)

filter_nomental <- filter_ot %>%
  filter(!id %in% id_mental) 
length(unique(filter_nomental$id)) # 6634

# Keep participants with complete data on covariates at baseline
id_cov <- filter_nomental %>%
  rowwise() %>%
  mutate(
    cov_miss = sum(is.na(c(age, male, atotb, lowedu, lbrf, nonmarried, hhres, smoken, weekdrink, phyinact, dis, adl_any, iadl)), na.rm = F)
  ) %>%
  ungroup() %>%
  mutate(
    with_cov = ifelse(cov_miss == 0, 1, 0)
  ) %>%
  group_by(id) %>%
  slice(1) %>%
  ungroup() %>%
  filter(with_cov == 1) %>%
  pull(id)

filter_cov <- filter_nomental %>%
  filter(id %in% id_cov) %>%
  rowwise() %>%
  mutate(
    cesd = sum(c(depres, flone, effort, sleepr, whappy, fsad, going, enlife), na.rm = F)
  ) %>%
  ungroup()
length(unique(filter_cov$id)) # 6587

table(filter_cov %>% group_by(id) %>% summarise(count = n()) %>% pull(count))

# Final dataset
## Replace with the baseline values
bl <- filter_cov %>% 
  group_by(id) %>% 
  slice(1) %>%
  ungroup() %>%
  mutate(
    .keep = "none",
    id, internet_freq, 
    age, male, lowedu, lowwealth = factor(reverse_code(ntile(atotb, 3))), lbrf, 
    nonmarried, hhres, smoken, weekdrink, phyinact,
    dis, adl_any, iadl
    )

final <- filter_cov %>%
  group_by(id) %>%
  mutate(
    fisrt = first(wave),
    cwave = wave - fisrt
  ) %>%
  ungroup() %>%
  mutate(
    .keep = "none",
    id, country, iwy, iwm, wave,
    cesd, shlt, satlife, 
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife),
    cwave
  ) %>%
  dplyr::select(
    id, country, iwy, iwm, wave,
    cesd, shlt, satlife,
    cesd_stand, shlt_stand, satlife_stand,
    cwave
  )

final_ifreq_hrs <- final %>% 
  left_join(., bl, by = "id") %>%
  mutate(
    id = str_c("hrs_", id)
  )

rm(bl, final)
rm(list = ls()[str_detect(string = ls(), pattern = "id_")])
object <- ls()[str_detect(string = ls(), pattern = "filter_")]
rm(list = object[!object %in% "filter_cov_iyes"])

```

## Cumulative Internet use

```{r}

# Keep participants aged >=51 years
id_50plus <- tidy_hrs %>%
  group_by(id) %>%
  slice(1) %>%
  ungroup() %>%
  filter(age >= 51) %>%
  pull(id)

filter_50plus <- tidy_hrs %>%
  filter(id %in% id_50plus)
length(unique(filter_50plus$id)) # 27333

# Keep participants with two consecutive wave complete data on internet use
id_2iobs <- filter_50plus %>%
  mutate(
    with_iyes = ifelse(!is.na(internet_yes), 1, 0)
  ) %>%
  group_by(id) %>%
  filter(n() >= 2) %>%
  slice(1:2) %>%
  mutate(
    wave_int = wave - lag(wave, default = first(wave)),
    t_with_iyes = cumsum(with_iyes)
  ) %>%
  filter(wave_int <= 3) %>%
  slice(n()) %>%
  filter(t_with_iyes == 2) %>%
  select(id, wave, wave_int, age, internet_yes, t_with_iyes) %>%
  ungroup() %>%
  pull(id)

filter_2iobs <- filter_50plus %>%
  filter(id %in% id_2iobs)
length(unique(filter_2iobs$id)) # 23171

table(filter_2iobs %>% group_by(id) %>% summarise(count = n()) %>% pull(count))

# Keep participants with complete data on outcomes at the third wave (baseline)
## Depressive symptoms
id_cesd_2w <- filter_2iobs %>%
  rowwise() %>%
  mutate(
    cesd_miss = sum(is.na(c(depres, flone, effort, sleepr, whappy, fsad, going, enlife)), na.rm = F)
  ) %>%
  ungroup() %>%
  mutate(
    with_cesd = ifelse(cesd_miss == 0, 1, 0)
  ) %>%
  group_by(id) %>%
  slice(2) %>%
  filter(with_cesd == 1) %>% 
  ungroup() %>%
  pull(id)

## Self-rated health
id_shlt_2w <- filter_2iobs %>%
  mutate(
    with_shlt = ifelse(!is.na(shlt), 1, 0)
  ) %>%
  group_by(id) %>%
  slice(2) %>%
  filter(with_shlt == 1) %>% 
  ungroup() %>%
  pull(id)

## Life satisfaction
id_satlife_2w <- filter_2iobs %>%
  mutate(
    with_satlife = ifelse(!is.na(satlife), 1, 0)
  ) %>%
  group_by(id) %>%
  slice(2) %>%
  filter(with_satlife == 1) %>% 
  ungroup() %>%
  pull(id)

id_ot_2w <- intersect(id_cesd_2w, id_shlt_2w) # 21606
id_ot_2w <- intersect(id_ot_2w, id_satlife_2w) # 21476

filter_ot_2w <- filter_2iobs %>%
  filter(id %in% id_ot_2w)
length(unique(filter_ot_2w$id)) # 21476

# Keep participants with at least one-wave complete data on outcomes over follow-ups
id_3obs <- filter_ot_2w %>%
  group_by(id) %>%
  filter(n() >= 3) %>%
  dplyr::slice(1) %>%
  ungroup() %>%
  pull(id)

filter_3obs <- filter_ot_2w %>%
  filter(id %in% id_3obs)
length(unique(filter_3obs$id)) # 17184

## Depressive symptoms
id_cesd <- filter_3obs %>%
  rowwise() %>%
  mutate(
    cesd_miss = sum(is.na(c(depres, flone, effort, sleepr, whappy, fsad, going, enlife)), na.rm = F)
  ) %>%
  ungroup() %>%
  mutate(
    with_cesd = ifelse(cesd_miss == 0, 1, 0)
  ) %>%
  group_by(id) %>%
  slice(3:n()) %>%
  mutate(
    t_with_cesd = cumsum(with_cesd)
    ) %>%
  slice(n()) %>%
  filter(t_with_cesd >= 1) %>% 
  ungroup() %>%
  pull(id)

## Self-rated health
id_shlt <- filter_3obs %>%
  mutate(
    with_shlt = ifelse(!is.na(shlt), 1, 0)
  ) %>%
  group_by(id) %>%
  slice(3:n()) %>%
  mutate(
    t_with_shlt = cumsum(with_shlt)
    ) %>%
  slice(n()) %>%
  filter(t_with_shlt >= 1) %>% 
  ungroup() %>%
  pull(id)

## Life satisfaction
id_satlife <- filter_3obs %>%
  mutate(
    with_satlife = ifelse(!is.na(satlife), 1, 0)
  ) %>%
  group_by(id) %>%
  slice(3:n()) %>%
  mutate(
    t_with_satlife = cumsum(with_satlife)
    ) %>%
  slice(n()) %>%
  filter(t_with_satlife >= 1) %>% 
  ungroup() %>%
  pull(id)

id_ot <- intersect(id_cesd, id_shlt) # 16832
id_ot <- intersect(id_ot, id_satlife) # 16798

filter_ot <- filter_3obs %>%
  filter(id %in% id_ot)
length(unique(filter_ot$id)) # 16798

# Keep participants without dementia and psychological diseases at baseline
id_mental <- filter_ot %>%
  group_by(id) %>%
  slice(2) %>%
  ungroup() %>%
  filter(memrye == "yes" | psyche == "yes") %>%
  pull(id)

filter_nomental <- filter_ot %>%
  filter(!id %in% id_mental) 
length(unique(filter_nomental$id)) # 13951

# Keep participants with complete data on covariates at baseline
id_cov <- filter_nomental %>%
  rowwise() %>%
  mutate(
    cov_miss = sum(is.na(c(age, male, atotb, lowedu, lbrf, nonmarried, hhres, smoken, weekdrink, phyinact, dis, adl_any, iadl)), na.rm = F)
  ) %>%
  ungroup() %>%
  mutate(
    with_cov = ifelse(cov_miss == 0, 1, 0) 
  ) %>%
  group_by(id) %>%
  slice(1) %>%
  ungroup() %>%
  filter(with_cov == 1) %>%
  pull(id)

filter_cov <- filter_nomental %>%
  filter(id %in% id_cov) %>%
  rowwise() %>%
  mutate(
    cesd = sum(c(depres, flone, effort, sleepr, whappy, fsad, going, enlife), na.rm = F)
  ) %>%
  ungroup()
length(unique(filter_cov$id)) # 13850

table(filter_cov %>% group_by(id) %>% summarise(count = n()) %>% pull(count))

# Final dataset
## Replace with the baseline values
icum <- filter_cov %>%
  mutate(
    internet_yes = as.numeric(internet_yes) - 1
    ) %>%
  group_by(id) %>%
  slice(1:2) %>%
  mutate(
    internet_cum = cumsum(internet_yes)
    ) %>% 
  slice(n()) %>%
  ungroup() %>%
  mutate(
    .keep = "none", id, internet_cum
  )

bl <- filter_cov %>% 
  group_by(id) %>% 
  slice(1) %>%
  ungroup() %>%
  mutate(
    .keep = "none",
    id, 
    age, male, lowedu, lowwealth = factor(reverse_code(ntile(atotb, 3))), lbrf, 
    nonmarried, hhres, smoken, weekdrink, phyinact,
    dis, adl_any, iadl
    ) %>%
  left_join(., icum, by = c("id"))

final <- filter_cov %>%
  group_by(id) %>%
  slice(2:n()) %>%
  mutate(
    fisrt = first(wave),
    cwave = wave - fisrt
  ) %>%
  ungroup() %>%
  mutate(
    .keep = "none",
    id, country, iwy, iwm, wave, 
    cesd, shlt, satlife, 
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife),
    cwave
  ) %>%
  dplyr::select(
    id, country, iwy, iwm, wave,
    cesd, shlt, satlife,
    cesd_stand, shlt_stand, satlife_stand,
    cwave
  )

final_icum_hrs <- final %>% 
  left_join(., bl, by = "id") %>%
  mutate(
    id = str_c("hrs_", id)
  )


rm(icum, bl, final)
rm(list = ls()[str_detect(string = ls(), pattern = "id_")])
object <- ls()[str_detect(string = ls(), pattern = "filter_")]
rm(list = object[!object %in% "filter_cov_iyes"])

```

## Internet use and genetic risk

```{r}

# Keep participants with PGS data
filter_pgs <- filter_cov_iyes %>%
  filter(id %in% hrs_pgs$hhidpn)
length(unique(filter_pgs$id)) # 10502

bl <- filter_pgs %>% 
  group_by(id) %>% 
  slice(1) %>%
  ungroup() %>%
  mutate(
    .keep = "none",
    id, depsymp_pgs, wellb_pgs,
    depsymp_pgs_quintile = ntile(depsymp_pgs, 5), 
    highdeprepgs = case_when(
      depsymp_pgs_quintile == 1 ~ "low",
      depsymp_pgs_quintile %in% c(2:4) ~ "intermediate",
      depsymp_pgs_quintile == 5 ~ "high",
      TRUE ~ NA_character_
    ),
    highdeprepgs = relevel(factor(highdeprepgs), ref = "low"),
    
    wellb_pgs_quintile = ntile(wellb_pgs, 5), 
    highwellbpgs = case_when(
      wellb_pgs_quintile == 5 ~ "low",
      wellb_pgs_quintile %in% c(2:4) ~ "intermediate",
      wellb_pgs_quintile == 1 ~ "high",
      TRUE ~ NA_character_
    ),
    highwellbpgs = relevel(factor(highwellbpgs), ref = "low"),
    
    internet_yes, 
    age, male, lowedu, lowwealth = factor(reverse_code(ntile(atotb, 3))), lbrf, 
    nonmarried, hhres, smoken, weekdrink, phyinact,
    dis, adl_any, iadl
    )

final <- filter_pgs %>%
  group_by(id) %>%
  mutate(
    fisrt = first(wave),
    cwave = wave - fisrt
  ) %>%
  ungroup() %>%
  mutate(
    .keep = "none",
    id, country, iwy, iwm, wave,
    cesd, shlt, satlife, 
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife),
    cwave
  ) %>%
  dplyr::select(
    id, country, iwy, iwm, wave,
    cesd, shlt, satlife,
    cesd_stand, shlt_stand, satlife_stand,
    cwave
  )

final_iyes_pgs_hrs <- final %>% 
  left_join(., bl, by = "id") %>%
  mutate(
    id = str_c("hrs_", id)
  ) %>% 
  select(
    id, country, iwy, iwm, wave, depsymp_pgs, wellb_pgs, 
    highdeprepgs, highwellbpgs,
    cesd, shlt, satlife,
    cesd_stand, shlt_stand, satlife_stand,
    cwave, 
    internet_yes, age, male, lowedu, lowwealth, lbrf, nonmarried, hhres, smoken, weekdrink, phyinact,
    dis, adl_any, iadl
    )

rm(bl, final)
rm(list = ls()[str_detect(string = ls(), pattern = "id_")])
rm(list = ls()[str_detect(string = ls(), pattern = "filter_")])

```


# Subgroup analyses: Internet use (yes/no)

## By age

```{r}

# 50-64 years
middle_iyes_hrs <- final_iyes_hrs %>%
  filter(age < 65) %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

# ≥65 years
old_iyes_hrs <- final_iyes_hrs %>%
  filter(age >= 65) %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

```

## By gender

```{r}

# Male
male_iyes_hrs <- final_iyes_hrs %>%
  filter(male == "male") %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

# Female
female_iyes_hrs <- final_iyes_hrs %>%
  filter(male == "female") %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

```

## By marital status

```{r}

# Married
married_iyes_hrs <- final_iyes_hrs %>%
  filter(nonmarried == "no") %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

# Unmarried
nonmarried_iyes_hrs <- final_iyes_hrs %>%
  filter(nonmarried == "yes") %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

```

## By education

```{r}

# Primary
pedu_iyes_hrs <- final_iyes_hrs %>%
  filter(lowedu == "primary") %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

# Secondary
sedu_iyes_hrs <- final_iyes_hrs %>%
  filter(lowedu == "secondary") %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

# Tertiary
tedu_iyes_hrs <- final_iyes_hrs %>%
  filter(lowedu == "tertiary") %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

```

## By household wealth

```{r}

# Low
lwealth_iyes_hrs <- final_iyes_hrs %>%
  filter(lowwealth == 3) %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

# Middle
mwealth_iyes_hrs <- final_iyes_hrs %>%
  filter(lowwealth == 2) %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

# High
hwealth_iyes_hrs <- final_iyes_hrs %>%
  filter(lowwealth == 1) %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

```

## By labor force status

```{r}

# Working
work_iyes_hrs <- final_iyes_hrs %>%
  filter(lbrf == "employed") %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

# Retired
retired_iyes_hrs <- final_iyes_hrs %>%
  filter(lbrf == "retired") %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

# Others
others_iyes_hrs <- final_iyes_hrs %>%
  filter(lbrf == "others") %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

```

## By current smoking 

```{r}

# Current smoking
smoke_iyes_hrs <- final_iyes_hrs %>%
  filter(smoken == "yes") %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

# No smoking
nosmoke_iyes_hrs <- final_iyes_hrs %>%
  filter(smoken == "no") %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

```

## By alcohol consumption

```{r}

# Weekly alcohol use
drink_iyes_hrs <- final_iyes_hrs %>%
  filter(weekdrink == "yes") %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

# Less than weekly alcohol use
nodrink_iyes_hrs <- final_iyes_hrs %>%
  filter(weekdrink == "no") %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )


```

## By physical activity

```{r}

# Physical inactivity
phyinact_iyes_hrs <- final_iyes_hrs %>%
  filter(phyinact == "yes") %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

# Physical activity
phyact_iyes_hrs <- final_iyes_hrs %>%
  filter(phyinact == "no") %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

```

## By ADL disability

```{r}

# ADL disability
adl_iyes_hrs <- final_iyes_hrs %>%
  filter(adl_any == "yes") %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

# No ADL limitation
noadl_iyes_hrs <- final_iyes_hrs %>%
  filter(adl_any == "no") %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

```

## By chronic conditions

```{r}

# ≥1 chronic conditions
dis_iyes_hrs <- final_iyes_hrs %>%
  filter(dis > 0) %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

# No chronic conditions
nodis_iyes_hrs <- final_iyes_hrs %>%
  filter(dis == 0) %>%
  select(!c(cesd_stand, shlt_stand, satlife_stand)) %>%
  mutate(
    cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
  )

```

# Sentivity analyses: Multiple imputation

## Internet use (yes/no)

```{r}

final_mi_iyes <- final_iyes_hrs %>%
  dplyr::select(!c(cesd_stand, shlt_stand, satlife_stand))

# Setting MICE arguments
predictorMatrix <- matrix(0, nrow = dim(final_mi_iyes)[2], ncol = dim(final_mi_iyes)[2])
colnames(predictorMatrix) <- colnames(final_mi_iyes)
rownames(predictorMatrix) <- colnames(final_mi_iyes)
row_pre <- which(rownames(predictorMatrix) %in% colnames(final_mi_iyes)[-c(1:5)])
col_pre <- which(colnames(predictorMatrix) %in% colnames(final_mi_iyes)[-c(1:5)])
predictorMatrix[row_pre, col_pre] <- 1
for(i in 6:dim(final_mi_iyes)[2]){ predictorMatrix[i,i]<-0 }

cores <- detectCores()
tic()
mi_iyes <- final_mi_iyes %>%
  futuremice(data = ., m = 20, maxit = 5, predictorMatrix = predictorMatrix, parallelseed = 12345, n.core = cores - 1)
toc()

mi_iyes_hrs <- list()

for(i in 1:20){
  mi_data <- mice::complete(mi_iyes, i) %>%
    mutate(
      cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
    )
  
  mi_iyes_hrs[[i]] <- mi_data
  
  rm(mi_data)
}

```

## Internet use frequency

```{r}

final_mi_ifreq <- final_ifreq_hrs %>%
  dplyr::select(!c(cesd_stand, shlt_stand, satlife_stand))

# Setting MICE arguments
predictorMatrix <- matrix(0, nrow = dim(final_mi_ifreq)[2], ncol = dim(final_mi_ifreq)[2])
colnames(predictorMatrix) <- colnames(final_mi_ifreq)
rownames(predictorMatrix) <- colnames(final_mi_ifreq)
row_pre <- which(rownames(predictorMatrix) %in% colnames(final_mi_ifreq)[-c(1:5)])
col_pre <- which(colnames(predictorMatrix) %in% colnames(final_mi_ifreq)[-c(1:5)])
predictorMatrix[row_pre, col_pre] <- 1
for(i in 6:dim(final_mi_ifreq)[2]){ predictorMatrix[i,i]<-0 }

cores <- detectCores()
tic()
mi_ifreq <- final_mi_ifreq %>%
  futuremice(data = ., m = 20, maxit = 5, predictorMatrix = predictorMatrix, parallelseed = 12345, n.core = cores - 1)
toc()

mi_ifreq_hrs <- list()

for(i in 1:20){
  mi_data <- mice::complete(mi_ifreq, i) %>%
    mutate(
      cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
    )
  
  mi_ifreq_hrs[[i]] <- mi_data
  
  rm(mi_data)
}

```

## Cumulative internet use

```{r}

final_mi_icum <- final_icum_hrs %>%
  dplyr::select(!c(cesd_stand, shlt_stand, satlife_stand))

# Setting MICE arguments
predictorMatrix <- matrix(0, nrow = dim(final_mi_icum)[2], ncol = dim(final_mi_icum)[2])
colnames(predictorMatrix) <- colnames(final_mi_icum)
rownames(predictorMatrix) <- colnames(final_mi_icum)
row_pre <- which(rownames(predictorMatrix) %in% colnames(final_mi_icum)[-c(1:5)])
col_pre <- which(colnames(predictorMatrix) %in% colnames(final_mi_icum)[-c(1:5)])
predictorMatrix[row_pre, col_pre] <- 1
for(i in 6:dim(final_mi_icum)[2]){ predictorMatrix[i,i]<-0 }

cores <- detectCores()
tic()
mi_icum <- final_mi_icum %>%
  futuremice(data = ., m = 20, maxit = 5, predictorMatrix = predictorMatrix, parallelseed = 12345, n.core = cores - 1)
toc()

mi_icum_hrs <- list()

for(i in 1:20){
  mi_data <- mice::complete(mi_icum, i) %>%
    mutate(
      cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
    )
  
  mi_icum_hrs[[i]] <- mi_data
  
  rm(mi_data)
}

```

## Internet use and genetic risk

```{r}

final_mi_iyes_pgs <- final_iyes_pgs_hrs %>%
  dplyr::select(!c(cesd_stand, shlt_stand, satlife_stand))

# Setting MICE arguments
predictorMatrix <- matrix(0, nrow = dim(final_mi_iyes_pgs)[2], ncol = dim(final_mi_iyes_pgs)[2])
colnames(predictorMatrix) <- colnames(final_mi_iyes_pgs)
rownames(predictorMatrix) <- colnames(final_mi_iyes_pgs)
row_pre <- which(rownames(predictorMatrix) %in% colnames(final_mi_iyes_pgs)[-c(1:8)])
col_pre <- which(colnames(predictorMatrix) %in% colnames(final_mi_iyes_pgs)[-c(1:8)])
predictorMatrix[row_pre, col_pre] <- 1
for(i in 9:dim(final_mi_iyes_pgs)[2]){ predictorMatrix[i,i]<-0 }

cores <- detectCores()
tic()
mi_iyes_pgs <- final_mi_iyes_pgs %>%
  futuremice(data = ., m = 20, maxit = 5, predictorMatrix = predictorMatrix, parallelseed = 12345, n.core = cores - 1)
toc()

mi_iyes_pgs_hrs <- list()

for(i in 1:20){
  mi_data <- mice::complete(mi_iyes_pgs, i) %>%
    mutate(
      cesd_stand = scale(cesd), shlt_stand = scale(shlt), satlife_stand = scale(satlife)
    )
  
  mi_iyes_pgs_hrs[[i]] <- mi_data
  
  rm(mi_data)
}

```

# Save data

```{r}

save(
  final_iyes_hrs, final_ifreq_hrs, final_icum_hrs, final_iyes_pgs_hrs, # Main analyses
  middle_iyes_hrs, old_iyes_hrs, male_iyes_hrs, female_iyes_hrs,
  pedu_iyes_hrs, sedu_iyes_hrs, tedu_iyes_hrs,
  lwealth_iyes_hrs, mwealth_iyes_hrs, hwealth_iyes_hrs,
  work_iyes_hrs, retired_iyes_hrs, others_iyes_hrs,
  smoke_iyes_hrs, nosmoke_iyes_hrs, drink_iyes_hrs, nodrink_iyes_hrs,
  married_iyes_hrs, nonmarried_iyes_hrs,
  phyinact_iyes_hrs, phyact_iyes_hrs, adl_iyes_hrs, noadl_iyes_hrs,
  dis_iyes_hrs, nodis_iyes_hrs, # Subgroup analyses
  mi_iyes_hrs, mi_ifreq_hrs, mi_icum_hrs, mi_iyes_pgs_hrs, # Multiple imputation analyses
  file = str_c(getwd(), "/data/processed/hrs_processed_data.RData", sep = "")
  )

```
